### 2018-01-04 Report/test.tex
Started to do paper.

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
\documentclass{llncs}
\usepackage{llncsdoc}
%
\begin{document}
    \title{Context Aware Virtual Assistant with
    Case-Based Conflict Resolution in
    Multi-User Smart Home Environment}
    \author{Bauyrzhan Ospan\inst{1} \and Kenzhegali Nurgaliyev\inst{1} \and Mario Jose Quinde Li Say Tan \inst{2} \and Nawaz Khan \inst{2}}
    \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@gmail.com}
    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{MQ093,N.X.Khan}@live.mdx.ac.uk}}
    \maketitle
    \begin{abstract}
        In this work we will examine and develop a Virtual Assistant which is the intelligence system that is used as a control
        interface of the Smart Home environment in the Farm Side Middlesex University laboratory. Specifically, the system is
        constructed to give multiple users ability to control devices` statuses by voice or text commands through the dialogue
        interface. Primarily, the main purpose of the system is to create user friendly interface with conflict resolution based
        on user cases. As a result, a Case-Based Reasoning algorithm was created with an innovative Ospan Matrix distance
        measurement module. In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice
        recognition and voice generation instruments were used to implement natural dialogue model of interactions with users.
        Moreover, the user friendly graphical web interface was developed. Further, a set of randomised double-blinded
        evaluation tests were established to check procedure of smart home control actions by multiple users.
    \end{abstract}
    \begin{keywords}
        Smart Home, Case-Based Reasoning, Context Awareness, Multiple User systems, Virtual Assistant
    \end{keywords}
    %
    \section{Introduction}
    %
    Managing a comfortable life could be a challenging task for people with special needs because some of them may need additional
    assistance to control electronic and electric devices in the living are [1]. The next group of users that probably seek
    assistance in Activities of Daily Life (ADL) is younger population while adults are away from home [1]. As a result,
    the Smart Home environments are developed to help users in controlling home and devices states with voice graphical
    interfaces [10] that are often called Virtual Assistants [1] or monitor behaviours of people
    with special needs [17] to classify changes in ADL that then alarm or notify relatives, health and care professionals
    and organizations [9]. Additional finding identified other techniques in the state of art.
    For example, in Smart Home systems there are Ontology-based platforms that allows to analyze user`s actions and
    perform context recognition [14] or visual tools for creating personal preferences table of each user based on semantics
    metadata [11]. As a consequence, majority of the researches is aimed to develop systems that helps alone living users.
    \\Despite number of
    researches in the Smart Home solutions that are automated, adaptive, multifunctional and interactive, there is a lack of
    investigations and development of systems that operates in a conflict resolution between multiple users with different
    needs and priorities. Some researchers in order to solve this dilemma developed context-aware automation platforms
    [13, 16] that resolves conflicts between automated devices such as fire alarms and automated door locks.
    On the other hand, these solutions resolves conflicts only between automated devices based on priorities of their rules.
    The next group of
    developers are focused on preference Rule-Based Reasoning (RBR) to resolve conflicts between users [1]. Even through
    these systems introduces efficient set of rules, they are not able to handle with adaptation to the new user cases or
    specific out-of-rule situations. \\To sum up
    state of art, there are number of systems that monitors and adapts to single users, resolves conflicts between devices
    in single user multi-agent environments and resolves conflicts between users based on if-else rules. On the contrary,
    there is a lack of the Virtual Assistants with an adaptive conflict resolution systems. \\
    In this research, we propose a Virtual Assistant (VA) system that controls Smart Home environment based on the user inputs via
    voice and text based dialogue graphical web user interface for multiple users. As a result, we developed number of
    subsystems to fully implement number of requests. First of all, interaction with the VA has to be user-friendly and
    natural as a human to human interaction. Second, the system has to be able to control and monitor state of the Smart
    Home devices. Finally, the VA has to manage to resolve conflicts between multiple users, and adapt to the new user cases.
    \\To cover all objectives, we introduced and developed the VA with next modules. Firstly, we have developed user friendly
    graphical interface based on web and cloud technologies to give to user intuitive way of interacting with the VA. For this
    reason, we used dynamic web framework, cloud voice recognition and generation technologies and animated emotional icons
    to mimicry natural face emotions in the dialogues. In addition to user friendly interface, we have developed and implemented
    adaptive natural language classification algorithms based on Artificial Neural Network (ANN) to make the VA understand
    different variates of the user commands and argumentation sentences. Therefore, users were able to speak to
    VA in the way they speak with other human. Secondly, we used Farm Side Middlesex University Smart Home laboratory and
    Smart Home devices control unit to manage and monitor Smart Home devices. In order that, we have developed and integrated
    software API to implement communication between Smart Home control unit and VA. The last but not the least, we have
    introduced and developed a conflict resolution system that used Case-Based Reasoning (CBR) to make a decision about
    conflict between multiple users. In order to make decision, VA identifies in dialogue form the argumentation of the user
    in performing an action, analyzes via Ospan Matrix distance k-nearest neighbour (kNN) algorithm similarities between
    this case and previous cases and chooses best-fit case. In other words, VA asks user to say why he or she wants to change
    device status if there conflicting instruction from other user and makes decision what to do with device based on users
    arguments and previous cases.
    \\Furthermore, we have established randomized double-blinded evaluation tests. In order to perform randomized double
    blinded experiment, we developed scenario creating sub-module. Firstly, it creates random scenario for tester by choosing
    conflicting device and arguments for tester by using crypto-secure randomise function based on operation system inner
    clocks. Secondly, it provides such instructions to testers that he or she was
    asked to provide command and arguments in their own words. As a result, it was hidden from us and testers scenarios till
    the beginning of the experiment. In addition, testers were asked to fill evaluation form. To conclude, feedback from
    testers are positive and only weak place of the system is accent recognition task.
    \\This paper presents Virtual Assistant in the multiple user Smart Home environment. The architecture of the system is
    described in the Section II. The system algorithms and sequences are described in the Section III. Section IV demonstrates
    our results and validation. Finally, Section V draws the conclusion and predictions for the future work.
    %
    \section{Architecture}
    %
    There will be architecture.
    %
    \subsection{Graphical User Interface}
    %
    Gui is described here.
    \subsection{Dialogue Component}
    %
    All about ANNs and dialogue manager.
    %
    \subsection{Rule-Based Reasoner}
    %
    \subsection{Case-Based Reasoner}
    %
    \subsection{Device Control Unit}
    %
    \section{Sequences}
    %
    There is sequence diagram.
    %
    \subsection{Regular Scenario}
    %
    \subsection{Conflict Scenario}
    %
    \section{Results and Validation}
    %
    \section{Conclusion and Future Work}
    \section{References}
    \label{refer}
    %
    There are three reference systems available; only one, of course,
    should be used for your contribution. With each system (by
    number only, by letter-number or by author-year) a reference list
    containing all citations in the
    text, should be included at the end of your contribution placing the
    \LaTeX{} environment \verb|thebibliography| there.
    For an overall information on that environment
    see the {\em \LaTeX{} User's Guide \& Reference
    Manual\/} by Leslie Lamport, p.~71.

    There is a special {\sc Bib}\TeX{} style for LLNCS that works along
    with the class: \verb|splncs.bst|
    -- call for it with a line \verb|\bibliographystyle{splncs}|.
    If you plan to use another {\sc Bib}\TeX{} style you are customed to,
    please specify the option \verb|[oribibl]| in the
    \verb|documentclass| line, like:
    \begin{verbatim}
        \documentclass[oribibl]{llncs}
    \end{verbatim}
    This will retain the original \LaTeX{} code for the bibliographic
    environment and the \verb|\cite| mechanism that many {\sc Bib}\TeX{}
    applications rely on.
    %
    \subsection{References by Letter-Number or by Number Only}
    %
    References are cited in the text -- using the \verb|\cite|
    command of \LaTeX{} -- by number or by letter-number in square
    brackets, e.g.\ [1] or [E1, S2], [P1], according to your use of the
    \verb|\bibitem| command in the \verb|thebibliography| environment. The
    coding is as follows: if you choose your own label for the sources by
    giving an optional argument to the \verb|\bibitem| command the citations
    in the text are marked with the label you supplied. Otherwise a simple
    numbering is done, which is preferred.
    \begin{verbatim}
        The results in this section are a refined version
        of \cite{clar:eke}; the minimality result of Proposition~14
        was the first of its kind.
    \end{verbatim}
    The above input produces the citation: ``\dots\ refined version of
    [CE1]; the min\-i\-mality\dots''. Then the \verb|\bibitem| entry of
    the \verb|thebibliography| environment should read:
    \begin{verbatim}
        \begin{thebibliography}{[MT1]}
            .
            .
            \bibitem[CE1]{clar:eke}
            Clarke, F., Ekeland, I.:
            Nonlinear oscillations and boundary-value problems for
            Hamiltonian systems.
            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
            .
            .
        \end{thebibliography}
    \end{verbatim}
    The complete bibliography looks like this:
    %
    \begin{thebibliography}{[MT1]}
        %
        \bibitem[CE1]{clar:eke}
        Clarke, F., Ekeland, I.:
        Nonlinear oscillations and
        boundary-value problems for Hamiltonian systems.
        Arch. Rat. Mech. Anal. 78, 315--333 (1982)
        %
        \bibitem[CE2]{clar:eke:2}
        Clarke, F., Ekeland, I.:
        Solutions p\'{e}riodiques, du
        p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
        Note CRAS Paris 287, 1013--1015 (1978)
        %
        \bibitem[MT1]{mich:tar}
        Michalek, R., Tarantello, G.:
        Subharmonic solutions with prescribed minimal
        period for nonautonomous Hamiltonian systems.
        J. Diff. Eq. 72, 28--55 (1988)
        %
        \bibitem[Ta1]{tar}
        Tarantello, G.:
        Subharmonic solutions for Hamiltonian
        systems via a $\bbbz_{p}$ pseudoindex theory.
        Annali di Matematica Pura (to appear)
        %
        \bibitem[Ra1]{rab}
        Rabinowitz, P.:
        On subharmonic solutions of a Hamiltonian system.
        Comm. Pure Appl. Math. 33, 609--633 (1980)
    \end{thebibliography}
    %
    \subsubsection*{Number-Only System.}
    %
    For this preferred system do not use the optional argument
    in the \verb|\bibitem| command: then, only numbers will
    appear for the citations in the text (enclosed in square brackets)
    as well as for the marks in your
    bibliography (here the number is only end-punctuated without
    square brackets).

    Subsequent citation numbers in the text are collapsed to ranges.
    Non-numeric and undefined labels are handled correctly but no sorting is
    done.

    E.g., \verb|\cite{n1,n3,n2,n3,n4,n5,foo,n1,n2,n3,?,n4,n5}| -- where
    \verb|n|$x$ is the key of the $x^{\mathrm{th}}$ \verb|\bibitem|
    command in sequence, \verb|foo| is the key of a \verb|\bibitem| with an
    optional argument, and \verb|?| is an undefined reference -- gives
    1,3,2-5,foo,1-3,?,4,5 as the citation reference.

    \begin{verbatim}
        \begin{thebibliography}{1}
            \bibitem {clar:eke}
            Clarke, F., Ekeland, I.:
            Nonlinear oscillations and boundary-value problems for
            Hamiltonian systems.
            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
        \end{thebibliography}
    \end{verbatim}
    %
    \subsection{Author-Year System}
    %
    References are cited in the text by name and year in parentheses
    and should look as follows:
    (Smith 1970, 1980), (Ekeland et al. 1985, Theorem 2), (Jones and Jaffe
    1986; Farrow 1988, Chap.\,2). If the name is part of the sentence
    only the year may appear in parentheses,
    e.g.\ Ekeland et al. (1985, Sect.\,2.1)
    The reference list should contain all citations occurring in the text,
    ordered alphabetically by surname (with initials following). If there
    are several works by the same author(s) the references should be listed
    in the appropriate order indicated below:
    \begin{alpherate}
        \setlength{\hfuzz}{5pt}
        \item
        One author: list works chronologically;
        \item
        Author and same co-author(s): list works chronologically;
        \item
        Author and different co-authors: list works alphabetically
        according to co-authors.
    \end{alpherate}
    If there are several works by the same author(s) and in the same year,
    but which are cited separately, they should be distinguished by the use
    of ``a'', ``b'' etc., e.g.\ (Smith 1982a), (Ekeland et al. 1982b).
    %
    \subsubsection*{How to Code Author-Year System.}
    %
    If you want to use this system you have to specify the option
    \verb|[citeauthoryear]| in the \verb|documentclass|, like:
    \begin{verbatim}
        \documentclass[citeauthoryear]{llncs}
    \end{verbatim}
    Write your citations in the text explicitly except for the year, leaving
    that up to \LaTeX{} with the \verb|\cite| command. Then give only the
    appropriate year as the optional argument (i.e. the label in square
    brackets) with the \verb|\bibitem| command(s).\\[2mm]
    {\itshape Sample Input}
    \begin{verbatim}
        The results in this section are a refined version
        of Clarke and Ekeland (\cite{clar:eke}); the minimality result of
        Proposition~14 was the first of its kind.
    \end{verbatim}
    The above input produces the citation: ``\dots\ refined version of
    Clarke and Ekeland (1982); the minimality\dots''. Then the
    \verb|\bibitem| entry of \verb|clar:eke| in the \verb|thebibliography|
    environment should read:
    \begin{verbatim}
        \begin{thebibliography}{}  % (do not forget {})
            .
            .
            \bibitem[1982]{clar:eke}
            Clarke, F., Ekeland, I.:
            Nonlinear oscillations and boundary-value problems for
            Hamiltonian systems.
            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
            .
            .
        \end{thebibliography}
    \end{verbatim}
    {\itshape Sample Output}
    \bibauthoryear
    %
\end{document}

### 2018-01-06 Paper/Paper.tex
First commit of Paper.

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
\documentclass{llncs}
\usepackage{llncsdoc}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{ {Images/} }
%
\begin{document}
    \title{Context Aware Virtual Assistant with
    Case-Based Conflict Resolution in
    Multi-User Smart Home Environment}
    \author{Bauyrzhan Ospan\inst{1} \and Kenzhegali Nurgaliyev\inst{1} \and Mario Jose Quinde Li Say Tan \inst{2} \and Nawaz Khan \inst{2}}
    \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@gmail.com}
    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{MQ093,N.X.Khan}@live.mdx.ac.uk}}
    \maketitle
    \begin{abstract}
        In this work we will examine and develop a Virtual Assistant which is the intelligence system that is used as a control
        interface of the Smart Home environment in the Farm Side Middlesex University laboratory. Specifically, the system is
        constructed to give multiple users ability to control devices` statuses by voice or text commands through the dialogue
        interface. Primarily, the main purpose of the system is to create user friendly interface with conflict resolution based
        on user cases. As a result, a Case-Based Reasoning algorithm was created with a k-Nearest Neighbor classification algorithm.
        In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice
        recognition and voice generation instruments were used to implement natural dialogue model of interactions with users.
        Moreover, the user friendly graphical web interface was developed. Further, a set of randomised double-blinded
        evaluation tests were established to check procedure of smart home control actions by multiple users.
    \end{abstract}
    \begin{keywords}
        Smart Home, Case-Based Reasoning, Context Awareness, Multiple User systems, Virtual Assistant
    \end{keywords}
    %
    \section{Introduction}
    %
    Managing a comfortable life could be a challenging task for people with special needs because some of them may need additional
    assistance to control electronic and electric devices in the living are [1]. The next group of users that probably seek
    assistance in Activities of Daily Life (ADL) is younger population while adults are away from home [1]. As a result,
    the Smart Home environments are developed to help users in controlling home and devices states with voice graphical
    interfaces [10] that are often called Virtual Assistants [1] or monitor behaviours of people
    with special needs [17] to classify changes in ADL that then alarm or notify relatives, health and care professionals
    and organizations [9]. Additional finding identified other techniques in the state of art.
    For example, in Smart Home systems there are Ontology-based platforms that allows to analyze user`s actions and
    perform context recognition [14] or visual tools for creating personal preferences table of each user based on semantics
    metadata [11]. As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\
    Despite number of
    researches in the Smart Home solutions that are automated, adaptive, multifunctional and interactive, there is a lack of
    investigations and development of systems that operates in a conflict resolution between multiple users with different
    needs and priorities. Some researchers in order to solve this dilemma developed context-aware automation platforms
    [13, 16] that resolves conflicts between automated devices such as fire alarms and automated door locks.
    On the other hand, these solutions resolves conflicts only between automated devices based on priorities of their rules.
    The next group of
    developers are focused on preference Rule-Based Reasoning (RBR) to resolve conflicts between users [1]. Even through
    these systems introduces efficient set of rules, they are not able to handle with adaptation to the new user cases or
    specific out-of-rule situations. \\
    To sum up
    state of art, there are number of systems that monitors and adapts to single users, resolves conflicts between devices
    in single user multi-agent environments and resolves conflicts between users based on if-else rules. On the contrary,
    there is a lack of the Virtual Assistants with an adaptive conflict resolution systems.\\
    In this research, we propose a Virtual Assistant (VA) system that controls Smart Home environment based on the user inputs via
    voice and text based dialogue graphical web user interface for multiple users. As a result, we developed number of
    subsystems to fully implement number of requests. First of all, interaction with the VA has to be user-friendly and
    natural as a human to human interaction. Second, the system has to be able to control and monitor state of the Smart
    Home devices. Finally, the VA has to manage to resolve conflicts between multiple users, and adapt to the new user cases.\\
    To cover all objectives, we introduced and developed the VA with next modules. Firstly, we have developed user friendly
    graphical interface based on web and cloud technologies to give to user intuitive way of interacting with the VA. For this
    reason, we used dynamic web framework, cloud voice recognition and generation technologies and animated emotional icons
    to mimicry natural face emotions in the dialogues. In addition to user friendly interface, we have developed and implemented
    adaptive natural language classification algorithms based on Artificial Neural Network (ANN) to make the VA understand
    different variates of the user commands and argumentation sentences, because they are effective algorithms for
    sentence classification [19]. Therefore, users were able to speak to
    VA in the way they speak with other human. Secondly, we used Farm Side Middlesex University Smart Home laboratory and
    Smart Home devices control unit to manage and monitor Smart Home devices. In order that, we have developed and integrated
    software API to implement communication between Smart Home control unit and VA. The last but not the least, we have
    introduced and developed a conflict resolution system that used Case-Based Reasoning (CBR) to make a decision about
    conflict between multiple users. In order to make decision, VA identifies in dialogue form the argumentation of the user
    in performing an action, analyzes via k-nearest neighbour (kNN) algorithm similarities between
    this case and previous cases and chooses best-fit case [4,7,15]. In other words, VA asks user to say why he or she wants to change
    device status if there conflicting instruction from other user and makes decision what to do with device based on users
    arguments and previous cases. Futhermore, arguments priorities was established by personal user preferences [3] because
    number of researches shows that the preference-based argumentation increases ability of the systems to meet user
    expectations [5].\\
    Furthermore, we have established randomized double-blinded evaluation tests. In order to perform randomized double
    blinded experiment, we developed scenario creating sub-module. Firstly, it creates random scenario for tester by choosing
    conflicting device and arguments for tester by using crypto-secure randomise function based on operation system inner
    clocks. Secondly, it provides such instructions to testers that he or she was
    asked to provide command and arguments in their own words. As a result, it was hidden from us and testers scenarios till
    the beginning of the experiment. In addition, testers were asked to fill evaluation form. To conclude, feedback from
    testers are positive and only weak place of the system is accent recognition task.\\
    This paper presents Virtual Assistant in the multiple user Smart Home environment. The Virtual Assistant was created
    to manage and monitor Smart Home environment by dialogue based interaction with users. Different machine learning
    algorithms and cloud technologies were implemented to meet project objectives. The main focus of the research was to
    develop adaptive conflict resolution system based on Case-Based Reasoner. The validation tests feedback is positive.
    The future direction of the work is to implement context-aware system that analyzes user behaviour and reports it as
    a case to the database of Case-Based Reasoner.\\
    This paper presents Virtual Assistant in the multiple user Smart Home environment. The architecture of the system is
    described in the Section II. The system algorithms and sequences are described in the Section III. Section IV demonstrates
    our results and validation. Finally, Section V draws the conclusion and predictions for the future work.
    %
    \section{Architecture}
    %
    Technical details of the system are given in this section.
    It consider architecture diagram of the system and explanation of all functional units called modules each
    or divided into the groups called components.
    \subsection{Overall}
    The architecture of the system is layered and modular.
    As a result, each functional part (module) of the system is designed to execute complete task and some of them are
    divided into components.
    The component is group of modules that performs complex task that consists of a number of simple tasks.
    For example, Order Classification and Reason Classification modules are grouped to Classification component.\\
    In addition, in order to give better understanding of the system, the architecture is divided into layers.
    Layer is functional components of the system that sequentially divides it into hierarchical groups that
    communicates only with layer above or layer below except Database layer.
    For example, Cloud API layer is consists of Speech Generation and Speech Recognition that communicate only with
    Front End layer and Core layer.\\
    Layer is demonstrated as white rectangle with grey icon and name in it.
    Web pages of the web interface is demonstrated as white colored box with blue drawing and text in it.
    Hexagonal icon with white image inside colored blue and text below is module of the system.
    White quadrilateral with grey illustration of device and it`s name underneath is icon of electronic device driven
    by Smart Home environment.
    Colored rectangle with text in the bottom right corner is illustration of components.
    All communication inside the system is demonstrated as arrows in the Fig.1.
    \footnote{Communication types and lifelines of the system is described in the Section III.}
    \begin{figure}
        \includegraphics[width=\textwidth]{arch.png}
        \caption[]{Architecture diagram of the system}
    \end{figure}
    \subsection{Graphical User Interface and Front End}
    The interface of the system is graphical web interface developed as web site.
    As a result, Graphical User Interface (GUI) is expressed by 3 functional and Login Pages that are listed below:
    \begin{enumerate}
        \item Login Page: Welcome interface - user chooses his or her account.
        \item Control Page: Dialogue interface - user communicates with system in form of dialogue by voice or text chat,
        gives orders \footnote{Order is command of the user given to the system. For example, turn off the light.} and reasons \footnote{Reason is argument given by the user to the system to justify his/her order. For example, turn off the light, because my eyes hurts.}.
        \item Rules \footnote{Rule is set of instructions given for system to do automatically. For example, system is obligated keep kettle turned off from 11:00 till 13:00 everyday because of energy saving issue.}
        Page: Rules editing interface - user edits list of instructions \footnote{Rules are discussed in the Section III.} given to the system.
        \item Preferences \footnote{Preference is set of issues that justifies orders of the user to the system. Every user type has its own priority level for preferences.} Page: Preferences editing interface - user edits his or her preferences \footnote{Preferences are discussed in the Section III.}.
    \end{enumerate}
    Flask Micro Web Framework is used as Front End controlling technology or Back End of the interface, because most of the project is coded by Python 3 language.
    \subsection{Cloud API}
    The function units of the Speech Generation and Speech Recognition were established via W3C Web Speech API \footnote{More information on https://w3c.github.io/speech-api/speechapi.html.}.
    They are JavaScript Application Programming Interfaces (API) that are used by most of the modern browsers.
    As a result, the system sends record of the user input to W3C API and it returns text that is the recognition of the record.
    Moreover, the system sends text to the browser of the user in such way that the browser automatically generates it into voice.
    The modules of the Speech Generation and Speech Recognition are inserted to the Dialogue component with Dilague Manager module.
    \subsection{Core System}
    Core System is main functional layer of the system.
    Consequently, functions as decision-making, dialogue compilation, text classification and device controlling are all executed in the modules inside the Core System layer.
    It consists of Dialogue Manager, Classification Component, Rule-Based Reasoner, Case-Based Reasoner and Device Control Unit.
    \subsection{Dialogue Manager}
    Dialogue Manager is one of the central modules of the system.
    Dialogue Manager receives phrases from the user and classifies it by Classification component and sends it to Rule-Based Reasoner.
    Based on the data from Rule-Based Reasoner and actions done by the system it sends human readable report or response to user via interface.
    In addition to Cloud API, Dialogue Manager is part of the Dialogue component that is the subsystem to communicate with user in natural way.
    Lastly, Dialogue Manager is set of if-else rules and dialogues database developed to pretend human-like speaking.
    \subsection{Classification Component}
    Classification component is group of two Classification modules that are Order and Reason Classification.
    Their function is to classify orders and reason from user input raw data.
    As a result, they need classification algorithm.\\
    Text classification is non-trivial complex task that is cannot be solved sequentially or by sequential algorithms artificial neural network systems (ANN) provides the better solution \cite{14}.
    Backpropagation as an ANS is very useful in recognizing complex patterns and performing nontrivial mapping functions.
    The figure below represents a simple Feed Forward Neural Network (FNN) diagram.
    The rounded objects represent the artificial neurons or processing elements of a neural network.
    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.
    Also every line of processing elements is a layer of a network.
    \begin{figure}
        \includegraphics[width=\textwidth]{ANN.png}
        \caption[]{Classification Neural Network Topology}
    \end{figure}
    \subsubsection{Topology of the Artificial Neural Network} is consists of Input, Output and Hidden layers.\\
    \em Input layer \em consist of input neurons that are binomial representation of the unique stemmed words (stemmed by LancasterStemmer from Natural Language Toolkit library) inside the text that is already cleaned from punctuation and meaningless words like articles.
    In a text document a word may exist in a different morphological variants.
    For example the word “love” may also exist in other morphological variants such as “loving”, “loved”.
    While these morphological variants are different word forms, that represent same concept.
    In text categorization and other similar tasks it is desirable to combine these morphological variants of the same word into one canonical form and represent it like vector that is called stemmed version.\\
    \em Output layer \em gives vector of possibilities that the text is inside of classes \footnote{Class is the group of reasons for Reason Classification and group of orders for Order Classification.}.
    The most possible class is the classification answer of the neural network.\\
    \em Hidden layer \em is the regression function of FNN, or layer between input and output layers.
    FNN applies a sequence of linear functions to the data.
    These functions are sigmoid linear transformation of the previous layer.
    As a result, it followed by a squashing nonlinearity
    While training the ANN (see below) it was concluded that the accuracy of the neural network does not significantly changes between one hidden layer neural network and multiple hidden layer neural network.
    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was calculated by 1000 iterations of Backpropogation training algorithm with standard training/test set especially created for this experiment.
    \begin{figure}
        \includegraphics[width=0.8\textwidth]{HL.png}
        \caption[]{Iterations of FNN with different Hidden Layer size, where horizontal line is number of neurons and vertical line is delta function percentage}
    \end{figure}
    \subsubsection{General Case: Trivial Reason.}
    In the next example user typed that he wants to change device status because he needs to finish a project about flu.
    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.
    The system normally does not accept any classification lower that 80\% possibility, and if user says something not
    correlated to the predefined preferences, the system will skip classification and ask again.
    \begin{example}
        User input is: \em I need to finish my project about flu \em \\
        System classified it as: \em [['Work', 0.99951473383654765], ['Health', 0.056650409249493161], ['Entertainment', 0.0011293354032656073], ['Energy', 1.4169164768812246e-05], ['Security', 1.238332260956378e-05], ['Food', 3.1674436013529605e-07]] \em
    \end{example}
    \subsubsection{General Case: Nontrivial Reason.}
    In the next example user typed "G'ylym janyp turg'an s'yraq" (Kazakh Language: Science is a burning candle).
    The system did not managed to classify this reason, because the system is tuned only for English.
    \begin{example}
        User input is: \em G'ylym janyp turg`an s`yraq \em\\
        System classified it as: \em [] (Null) \em
    \end{example}
    \subsection{Training of FNN}
    It was used Backpropogation method for artificial neural network weights of the synapses optimisation.
    The Backpropagation learning rule based on supervised learning \cite{14}.
    In order to train neural network, a set of training documents and a specification of the pre-defined categories the documents belong to are required.
    Training and testing sets were created specially for this experiment.
    There were used common English phrases and their synonyms to create set of sentences and their class.
    During training, the connection weights of the neural network are initialized to random values.
    The training examples in the training set are then presented to the neural network classifier in random order, and the connection weights are adjusted according to the Backpropagation learning rule.
    This process is repeated until the learning error falls below a predefined tolerance level (99.95\%).
    Below there is an example of the training of the Reason Classifier.
    \begin{example}
        Input matrix: 260x198 Output matrix: 1x6\\
        delta after 10000 iterations:0.00195103818538\\
        delta after 20000 iterations:0.00132469839464\\
        delta after 30000 iterations:0.00105975676227\\
        delta after 40000 iterations:0.000905619354028\\
        delta after 50000 iterations:0.000802125845806\\
        delta after 60000 iterations:0.000726645045015\\
        delta after 70000 iterations:0.000668536139359\\
        delta after 80000 iterations:0.000622059862315\\
        delta after 90000 iterations:0.000583815748815\\
        delta after 100000 iterations:0.000551645861196\\
        saved synapses to: ./include/synapses.json\\
        processing time: 103.20042490959167 seconds\\
    \end{example}
    \subsection{Rule-Based Reasoner}
    Rule-Based Reasoner receives data about the user`s order and compares it with rules in the Database and actual status of the devices.
    Core of the Rule-Based Reasoner is the set of if-else rules:
    \begin{enumerate}
        \item If status of device equals to status that user already wants: return similarity response; else: go further.
        \item If there is conflict between rule and user`s order: send task to Case-Based Reasoner; else: send command to Device COntrol Unit.
    \end{enumerate}
    \subsection{Case-Based Reasoner}

    \section{Sequences}
    %
    \section{Results and Validation}
    %
    \section{Conclution}
    \section{References}
    \begin{thebibliography}{1}
        \bibitem {1}
        Alirezaie, M., Renoux, J., Köckemann, U., Kristoffersson, A., Karlsson, L., Blomqvist, E., Tsiftes, N., Voigt, T., Loutfi, A.: An Ontology-based Context-aware System for Smart Homes: E-care@home. Sensors. 17, 1586 (2017).

        \bibitem {2}
        Aztiria, A., Augusto, J., Basagoiti, R., Izaguirre, A., Cook, D.: Learning Frequent Behaviors of the Users in Intelligent Environments. IEEE Transactions on Systems, Man, and Cybernetics: Systems. 43, 1265-1278 (2013).

        \bibitem {3}
        Fleury, A., Vacher, M., Noury, N.: SVM-Based Multimodal Classification of Activities of Daily Living in Health Smart Homes: Sensors, Algorithms, and First Experimental Results. IEEE Transactions on Information Technology in Biomedicine. 14, 274-283 (2010).

        \bibitem {4}
        Göynügür, E., Bernardini, S., de Mel, G., Talamadupula, K., Şensoy, M.: Policy Conflict Resolution in IoT via Planning. Advances in Artificial Intelligence. 169-175 (2017).

        \bibitem {5}
        Hadj, R., Hamon, C., Chollet, S., Vega, G., Lalanda, P.: Context-based conflict management in pervasive platforms. 2017 IEEE International Conference on Pervasive Computing and Communications Workshops (PerCom Workshops). (2017).

        \bibitem {6}
        Kabir, M., Hoque, M., Seo, H., Yang, S.: Machine Learning Based Adaptive Context-Aware System for Smart Home Environment, https://pdfs.semanticscholar.org/8cf5/fe5062727744f5429bb34d9c0bd24f439ee6.pdf.

        \bibitem {7}
        Khan, N., Alegre, U., Kramer, D., Augusto, J.: Is ‘Context-Aware Reasoning = Case-Based Reasoning’?. Modeling and Using Context. 418-431 (2017).

        \bibitem {8}
        Mayer, S., Inhelder, N., Verborgh, R., Van de Walle, R., Mattern, F.: Configuration of smart environments made simple: Combining visual modeling with semantic metadata and reasoning. 2014 International Conference on the Internet of Things (IOT). (2014).

        \bibitem {9}
        Nurgaliyev, K., Mauro, D., Khan, N., Augusto, J.: Improved Multi-user Interaction in a Smart Environment Through a Preference-Based Conflict Resolution Virtual Assistant. 2017 International Conference on Intelligent Environments (IE). (2017).

        \bibitem {10}
        Oguego, C., Augusto, J., Muñ`oz, A., Springett, M.: A survey on managing users’ preferences in ambient intelligence. Universal Access in the Information Society. (2017).

        \bibitem {11}
        Oguego, C., Augusto, J., Muñoz, A., Springett, M.: Using argumentation to manage users’ preferences. Future Generation Computer Systems. 81, 235-243 (2018).

        \bibitem {12}
        Ospan, B.: Simulation of a Simple Bio-Mimetic Robot with Neuromorphic Control System and Optimization Based on the Genetic Algorithm. International Journal of Innovations in Engineering and Technology. 8, 59-65 (2017).
        \bibitem {13}
        Portet, F., Vacher, M., Golanski, C., Roux, C., Meillon, B.: Design and evaluation of a smart home voice interface for the elderly: acceptability and objection aspects. Personal and Ubiquitous Computing. 17, 127-144 (2011).

        \bibitem {14}
        Ramasundaram, S., Victor, S.: Text Categorization by Backpropagation Network, http://www.ijcaonline.org/archives/volume8/number6/1217-1754.

        \bibitem {15}
        Reichherzer, T., Satterfield, S., Belitsos, J., Chudzynski, J., Watson, L.: An Agent-Based Architecture for Sensor Data Collection and Reasoning in Smart Home Environments for Independent Living. Advances in Artificial Intelligence. 15-20 (2016).

        \bibitem {16}
        Siolas, G., Caridakis, G., Mylonas, P., Kollias, S., Stafylopatis, A.: Context-Aware User Modeling and Semantic Interoperability in Smart Home Environments. 2013 8th International Workshop on Semantic and Social Media Adaptation and Personalization. (2013).

        \bibitem {17}
        Weinberger, K., Lawrence, S.: Distance Metric Learning for Large Margin Nearest Neighbor Classification. Journal of Machine Learning Research. 10, 207-244 (2009).

    \end{thebibliography}

\end{document}

### 2018-01-06 Report/test.tex
First commit of Paper.

@@
         interface. Primarily, the main purpose of the system is to create user friendly interface with conflict resolution based
-        on user cases. As a result, a Case-Based Reasoning algorithm was created with an innovative Ospan Matrix distance
-        measurement module. In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice
+        on user cases. As a result, a Case-Based Reasoning algorithm was created with a k-Nearest Neighbor classification algorithm.
+        In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice
         recognition and voice generation instruments were used to implement natural dialogue model of interactions with users.
@@
     perform context recognition [14] or visual tools for creating personal preferences table of each user based on semantics
-    metadata [11]. As a consequence, majority of the researches is aimed to develop systems that helps alone living users.
-    \\Despite number of
+    metadata [11]. As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\
+    Despite number of
     researches in the Smart Home solutions that are automated, adaptive, multifunctional and interactive, there is a lack of
@@
     these systems introduces efficient set of rules, they are not able to handle with adaptation to the new user cases or
-    specific out-of-rule situations. \\To sum up
+    specific out-of-rule situations. \\
+    To sum up
     state of art, there are number of systems that monitors and adapts to single users, resolves conflicts between devices
     in single user multi-agent environments and resolves conflicts between users based on if-else rules. On the contrary,
-    there is a lack of the Virtual Assistants with an adaptive conflict resolution systems. \\
+    there is a lack of the Virtual Assistants with an adaptive conflict resolution systems.
+    \section{Methodology}
     In this research, we propose a Virtual Assistant (VA) system that controls Smart Home environment based on the user inputs via
@@
     natural as a human to human interaction. Second, the system has to be able to control and monitor state of the Smart
-    Home devices. Finally, the VA has to manage to resolve conflicts between multiple users, and adapt to the new user cases.
-    \\To cover all objectives, we introduced and developed the VA with next modules. Firstly, we have developed user friendly
+    Home devices. Finally, the VA has to manage to resolve conflicts between multiple users, and adapt to the new user cases.\\
+    To cover all objectives, we introduced and developed the VA with next modules. Firstly, we have developed user friendly
     graphical interface based on web and cloud technologies to give to user intuitive way of interacting with the VA. For this
@@
     adaptive natural language classification algorithms based on Artificial Neural Network (ANN) to make the VA understand
-    different variates of the user commands and argumentation sentences. Therefore, users were able to speak to
+    different variates of the user commands and argumentation sentences, because they are effective algorithms for
+    sentence classification [19]. Therefore, users were able to speak to
     VA in the way they speak with other human. Secondly, we used Farm Side Middlesex University Smart Home laboratory and
@@
     conflict between multiple users. In order to make decision, VA identifies in dialogue form the argumentation of the user
-    in performing an action, analyzes via Ospan Matrix distance k-nearest neighbour (kNN) algorithm similarities between
-    this case and previous cases and chooses best-fit case. In other words, VA asks user to say why he or she wants to change
+    in performing an action, analyzes via k-nearest neighbour (kNN) algorithm similarities between
+    this case and previous cases and chooses best-fit case [4,7,15]. In other words, VA asks user to say why he or she wants to change
     device status if there conflicting instruction from other user and makes decision what to do with device based on users
-    arguments and previous cases.
-    \\Furthermore, we have established randomized double-blinded evaluation tests. In order to perform randomized double
+    arguments and previous cases. Futhermore, arguments priorities was established by personal user preferences [3] because
+    number of researches shows that the preference-based argumentation increases ability of the systems to meet user
+    expectations [5].
+    \section{Validation}
+    Furthermore, we have established randomized double-blinded evaluation tests. In order to perform randomized double
     blinded experiment, we developed scenario creating sub-module. Firstly, it creates random scenario for tester by choosing
@@
     the beginning of the experiment. In addition, testers were asked to fill evaluation form. To conclude, feedback from
-    testers are positive and only weak place of the system is accent recognition task.
-    \\This paper presents Virtual Assistant in the multiple user Smart Home environment. The architecture of the system is
-    described in the Section II. The system algorithms and sequences are described in the Section III. Section IV demonstrates
-    our results and validation. Finally, Section V draws the conclusion and predictions for the future work.
-    %
-    \section{Architecture}
-    %
-    There will be architecture.
-    %
-    \subsection{Graphical User Interface}
-    %
-    Gui is described here.
-    \subsection{Dialogue Component}
-    %
-    All about ANNs and dialogue manager.
-    %
-    \subsection{Rule-Based Reasoner}
-    %
-    \subsection{Case-Based Reasoner}
-    %
-    \subsection{Device Control Unit}
-    %
-    \section{Sequences}
-    %
-    There is sequence diagram.
-    %
-    \subsection{Regular Scenario}
-    %
-    \subsection{Conflict Scenario}
-    %
-    \section{Results and Validation}
-    %
-    \section{Conclusion and Future Work}
+    testers are positive and only weak place of the system is accent recognition task.\\
+    This paper presents Virtual Assistant in the multiple user Smart Home environment. The Virtual Assistant was created
+    to manage and monitor Smart Home environment by dialogue based interaction with users. Different machine learning
+    algorithms and cloud technologies were implemented to meet project objectives. The main focus of the research was to
+    develop adaptive conflict resolution system based on Case-Based Reasoner. The validation tests feedback is positive.
+    The future direction of the work is to implement context-aware system that analyzes user behaviour and reports it as
+    a case to the database of Case-Based Reasoner.
+
     \section{References}
-    \label{refer}
-    %
-    There are three reference systems available; only one, of course,
-    should be used for your contribution. With each system (by
-    number only, by letter-number or by author-year) a reference list
-    containing all citations in the
-    text, should be included at the end of your contribution placing the
-    \LaTeX{} environment \verb|thebibliography| there.
-    For an overall information on that environment
-    see the {\em \LaTeX{} User's Guide \& Reference
-    Manual\/} by Leslie Lamport, p.~71.
+    \bibliographystyle{llncs}
+    \bibliography{./bib.bib}
 
-    There is a special {\sc Bib}\TeX{} style for LLNCS that works along
-    with the class: \verb|splncs.bst|
-    -- call for it with a line \verb|\bibliographystyle{splncs}|.
-    If you plan to use another {\sc Bib}\TeX{} style you are customed to,
-    please specify the option \verb|[oribibl]| in the
-    \verb|documentclass| line, like:
-    \begin{verbatim}
-        \documentclass[oribibl]{llncs}
-    \end{verbatim}
-    This will retain the original \LaTeX{} code for the bibliographic
-    environment and the \verb|\cite| mechanism that many {\sc Bib}\TeX{}
-    applications rely on.
-    %
-    \subsection{References by Letter-Number or by Number Only}
-    %
-    References are cited in the text -- using the \verb|\cite|
-    command of \LaTeX{} -- by number or by letter-number in square
-    brackets, e.g.\ [1] or [E1, S2], [P1], according to your use of the
-    \verb|\bibitem| command in the \verb|thebibliography| environment. The
-    coding is as follows: if you choose your own label for the sources by
-    giving an optional argument to the \verb|\bibitem| command the citations
-    in the text are marked with the label you supplied. Otherwise a simple
-    numbering is done, which is preferred.
-    \begin{verbatim}
-        The results in this section are a refined version
-        of \cite{clar:eke}; the minimality result of Proposition~14
-        was the first of its kind.
-    \end{verbatim}
-    The above input produces the citation: ``\dots\ refined version of
-    [CE1]; the min\-i\-mality\dots''. Then the \verb|\bibitem| entry of
-    the \verb|thebibliography| environment should read:
-    \begin{verbatim}
-        \begin{thebibliography}{[MT1]}
-            .
-            .
-            \bibitem[CE1]{clar:eke}
-            Clarke, F., Ekeland, I.:
-            Nonlinear oscillations and boundary-value problems for
-            Hamiltonian systems.
-            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
-            .
-            .
-        \end{thebibliography}
-    \end{verbatim}
-    The complete bibliography looks like this:
-    %
-    \begin{thebibliography}{[MT1]}
-        %
-        \bibitem[CE1]{clar:eke}
-        Clarke, F., Ekeland, I.:
-        Nonlinear oscillations and
-        boundary-value problems for Hamiltonian systems.
-        Arch. Rat. Mech. Anal. 78, 315--333 (1982)
-        %
-        \bibitem[CE2]{clar:eke:2}
-        Clarke, F., Ekeland, I.:
-        Solutions p\'{e}riodiques, du
-        p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
-        Note CRAS Paris 287, 1013--1015 (1978)
-        %
-        \bibitem[MT1]{mich:tar}
-        Michalek, R., Tarantello, G.:
-        Subharmonic solutions with prescribed minimal
-        period for nonautonomous Hamiltonian systems.
-        J. Diff. Eq. 72, 28--55 (1988)
-        %
-        \bibitem[Ta1]{tar}
-        Tarantello, G.:
-        Subharmonic solutions for Hamiltonian
-        systems via a $\bbbz_{p}$ pseudoindex theory.
-        Annali di Matematica Pura (to appear)
-        %
-        \bibitem[Ra1]{rab}
-        Rabinowitz, P.:
-        On subharmonic solutions of a Hamiltonian system.
-        Comm. Pure Appl. Math. 33, 609--633 (1980)
-    \end{thebibliography}
-    %
-    \subsubsection*{Number-Only System.}
-    %
-    For this preferred system do not use the optional argument
-    in the \verb|\bibitem| command: then, only numbers will
-    appear for the citations in the text (enclosed in square brackets)
-    as well as for the marks in your
-    bibliography (here the number is only end-punctuated without
-    square brackets).
-
-    Subsequent citation numbers in the text are collapsed to ranges.
-    Non-numeric and undefined labels are handled correctly but no sorting is
-    done.
-
-    E.g., \verb|\cite{n1,n3,n2,n3,n4,n5,foo,n1,n2,n3,?,n4,n5}| -- where
-    \verb|n|$x$ is the key of the $x^{\mathrm{th}}$ \verb|\bibitem|
-    command in sequence, \verb|foo| is the key of a \verb|\bibitem| with an
-    optional argument, and \verb|?| is an undefined reference -- gives
-    1,3,2-5,foo,1-3,?,4,5 as the citation reference.
-
-    \begin{verbatim}
-        \begin{thebibliography}{1}
-            \bibitem {clar:eke}
-            Clarke, F., Ekeland, I.:
-            Nonlinear oscillations and boundary-value problems for
-            Hamiltonian systems.
-            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
-        \end{thebibliography}
-    \end{verbatim}
-    %
-    \subsection{Author-Year System}
-    %
-    References are cited in the text by name and year in parentheses
-    and should look as follows:
-    (Smith 1970, 1980), (Ekeland et al. 1985, Theorem 2), (Jones and Jaffe
-    1986; Farrow 1988, Chap.\,2). If the name is part of the sentence
-    only the year may appear in parentheses,
-    e.g.\ Ekeland et al. (1985, Sect.\,2.1)
-    The reference list should contain all citations occurring in the text,
-    ordered alphabetically by surname (with initials following). If there
-    are several works by the same author(s) the references should be listed
-    in the appropriate order indicated below:
-    \begin{alpherate}
-        \setlength{\hfuzz}{5pt}
-        \item
-        One author: list works chronologically;
-        \item
-        Author and same co-author(s): list works chronologically;
-        \item
-        Author and different co-authors: list works alphabetically
-        according to co-authors.
-    \end{alpherate}
-    If there are several works by the same author(s) and in the same year,
-    but which are cited separately, they should be distinguished by the use
-    of ``a'', ``b'' etc., e.g.\ (Smith 1982a), (Ekeland et al. 1982b).
-    %
-    \subsubsection*{How to Code Author-Year System.}
-    %
-    If you want to use this system you have to specify the option
-    \verb|[citeauthoryear]| in the \verb|documentclass|, like:
-    \begin{verbatim}
-        \documentclass[citeauthoryear]{llncs}
-    \end{verbatim}
-    Write your citations in the text explicitly except for the year, leaving
-    that up to \LaTeX{} with the \verb|\cite| command. Then give only the
-    appropriate year as the optional argument (i.e. the label in square
-    brackets) with the \verb|\bibitem| command(s).\\[2mm]
-    {\itshape Sample Input}
-    \begin{verbatim}
-        The results in this section are a refined version
-        of Clarke and Ekeland (\cite{clar:eke}); the minimality result of
-        Proposition~14 was the first of its kind.
-    \end{verbatim}
-    The above input produces the citation: ``\dots\ refined version of
-    Clarke and Ekeland (1982); the minimality\dots''. Then the
-    \verb|\bibitem| entry of \verb|clar:eke| in the \verb|thebibliography|
-    environment should read:
-    \begin{verbatim}
-        \begin{thebibliography}{}  % (do not forget {})
-            .
-            .
-            \bibitem[1982]{clar:eke}
-            Clarke, F., Ekeland, I.:
-            Nonlinear oscillations and boundary-value problems for
-            Hamiltonian systems.
-            Arch. Rat. Mech. Anal. 78, 315--333 (1982)
-            .
-            .
-        \end{thebibliography}
-    \end{verbatim}
-    {\itshape Sample Output}
-    \bibauthoryear
-    %
 \end{document}

### 2018-01-06 Paper/Reference.py

@@ -1,0 +1,12 @@
+#!/usr/bin/python3
+# -*- coding: UTF-8 -*-
+with open("./references.txt", 'r') as f:
+    refs = f.readlines()
+    refs = sorted(refs)
+with open("./references.txt", 'w') as w:
+    w.write("\\begin{thebibliography}{1} \n")
+    for k in range(len(refs)):
+        string = "\\bibitem {" + str(k + 1) + "}\n" + str(refs[k]) + "\n"
+        w.write(string)
+    w.write("\\end{thebibliography} \n")
+print("Finished")

### 2018-01-09 Paper/Paper.tex
Deleted old CBR. Updated Wiki page.

@@
     Multi-User Smart Home Environment}
-    \author{Bauyrzhan Ospan\inst{1} \and Kenzhegali Nurgaliyev\inst{1} \and Mario Jose Quinde Li Say Tan \inst{2} \and Nawaz Khan \inst{2}}
-    \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@gmail.com}
-    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{MQ093,N.X.Khan}@live.mdx.ac.uk}}
+    \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Jose Quinde Li Say Tan \inst{2} \and Kenzhegali Nurgaliyev \inst{1}}
+    \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@nu.edu.kz}
+    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{N.X.Khan,J.Augusto,MQ093}@live.mdx.ac.uk}}
     \maketitle
@@
     \begin{keywords}
-        Smart Home, Case-Based Reasoning, Context Awareness, Multiple User systems, Virtual Assistant
+        Case-Based Reasoning, Context Awareness, Multiple User systems, Smart Home, Virtual Assistant
     \end{keywords}
@@
     \subsection{Case-Based Reasoner}
-
+    Case-Based Reasoner works by finding the lowest distance of input case to the cases inside the database.
+    CBR is an artificial intelligence approach to determine a similarity amongst a set of cases.
+    This method indexes cases from history of the system usage and retrieves best similar case by measurement of distance between the input case and past cases.
+    The result of finding best match is stored inside the cases database to update the cases database and adapt old solution to the new variables and environment.
+    CBR is based on a suggestion that the similar cases have similar solution.
+    The decisions in our system is binary (0 for not change device status, 1 for change it).
+    As a result, it is accessible that CBR assumption works in our system.
+    Most of the CBR systems uses k-nearest neighbour algorithm.
+    The accuracy of this classification algorithm seriously depends on the metrics or system of measurement used to compute distances between different cases.
+    The nearest neighbour algorithm determines the similarity or dissimilarity of a new case with the case base and follows a cyclical process of Retrieve-Reuse-Revise-Retain.
+    In our case inputs to the system are in different system of measurements.
+    Cases in the system are build on preferences and priority of users of the system.
+    Both two variables have different basis.
+    As a result, standard Euclidean Distance cannot be used as a distance measurement algorithm.
+    It was proposed to use Mahalanobis distance that is the global linear transformation tool of the input spaces of the cases from different classes separated by a large margins.
+    Using of Mahalanobis distance significantly increases kNN accuracy.
+    In addition, there was used a Genetic Algorithm to find best value of Mahalanobis covariance matrix.
+    It is was set nearly 11 quadrillion types of mutations patterns.
+    The covariance matrix was used as genome of each genome in the epoch.
+    As a result, each epoch system chooses best accuracy model and mutates it`s one hundred children with different not significant mutations in the genome.
+    Then the system iterate again while accuracy of the best model (king) will not reach threshold value.
+    \subsection{Device Control Unit}
+    Smart Home environment of the Farm Side Middlesex University is driven by Vera Secure system.
+    In consequence, we developed API to communicate with it.
+    Vera Secure system has own web interface.
+    In order to communicate with it, we sending and receiving GET and POST requests.
+    Special POST requests changes status of the devices, which are kettle and light in our experiment.
+    Next, updating information about device statuses is done by parsing response from special GET request sent to the Vera Secure server.
     \section{Sequences}
     %
+    Sequences inside the system are mentioned in this chapter.
+    \subsection{Terminology}
+    We used user types and preference system proposed by \cite{9} .
+    As a result, different group of users were outlined and divided by age.
+    Moreover, we declared updated system of preferences.
+    \begin{table}
+        \caption{List of users and preferences}
+        \begin{tabular}{llllll}
+            \hline\noalign{\smallskip}
+            User types & Preferences (positions 0,1,2,3,4,5)\\
+            \noalign{\smallskip}
+            \hline
+            \noalign{\smallskip}
+            Adult (26-69 ages) & Security, Health, Work, Food, Energy, Entertainment\\
+            Elderly (older 70) & Health, Security, Food, Energy, Entertainment, Work\\
+            Young (up to 25 ages) & Security, Work, Entertainment, Health, Food, Energy\\
+            \hline
+        \end{tabular}
+    \end{table}
+
+    \subsection{Regular Case}
+    \subsection{Conflicting Case}
     \section{Results and Validation}

### 2018-01-09 CBR/CBR.py

@@ -116,3 +116,4 @@ def main(usertypein, usertypeout, reasonin, reasonout):
             'id': 0}
     # Returning result
     return Calculate(Mahalanobis, test)
+

### 2018-01-09 CBR/CBRevaluation.py

@@ -1,235 +1,0 @@
-#!/usr/bin/python3
-# -*- coding: UTF-8 -*-
-import operator
-from itertools import permutations
-import itertools
-import random
-import numpy as np
-import time
-import datetime
-import pymysql
-import pandas as pd
-import scipy as sp
-from scipy.spatial.distance import mahalanobis
-import copy
-from random import shuffle
-
-# Connect to db
-con = pymysql.connect(host='0.0.0.0', unix_socket='/tmp/mysql.sock', user="root", passwd="123", db='virtass')
-cur = con.cursor(pymysql.cursors.DictCursor)
-
-# Put coefficients of reasons and preferences
-usersList = {"adult": 1, "young": 2, "elder": 3}
-
-
-# Function that loads cases and preferences
-def load():
-    with con:
-        cur.execute('SELECT * FROM cases')
-        casesRaw = list(cur.fetchall())
-        cur.execute('SELECT * FROM preferences')
-        prefRaw = list(cur.fetchall())
-
-        # For each element of table is stored into list of training and test sets
-        for k in range(len(casesRaw)):
-            for l in range(len(prefRaw)):
-                # Each of the reason is parsed inside global variable and coefficients are put
-                if casesRaw[k]["usertypeIN"] == prefRaw[l]["usertype"]:
-                    try:
-                        n = float(prefRaw[l][str(casesRaw[k]["reasonIN"])])
-                        casesRaw[k]["reasonIN"] = n
-                    except KeyError:
-                        n = 10
-                if casesRaw[k]["usertypeOUT"] == prefRaw[l]["usertype"]:
-                    try:
-                        n = prefRaw[l][str(casesRaw[k]["reasonOUT"])]
-                        casesRaw[k]["reasonOUT"] = n
-                    except KeyError:
-                        n = 10
-            # Put coefficients from global variables to lists
-            try:
-                casesRaw[k]["usertypeIN"] = usersList[casesRaw[k]["usertypeIN"]]
-                casesRaw[k]["usertypeOUT"] = usersList[casesRaw[k]["usertypeOUT"]]
-            except KeyError:
-                n = 10
-    # Creating training and test set and return it
-    training = casesRaw
-    test = casesRaw
-    return training, test
-
-
-# Function that loads cases and without preferences
-def loadOLD():
-    with con:
[…]

### 2018-01-09 CBR/CBRold.py

@@ -1,240 +1,0 @@
-#!/usr/bin/python3
-# -*- coding: UTF-8 -*-
-import operator
-from itertools import permutations
-import itertools
-import random
-import numpy as np
-import time
-import datetime
-import pymysql
-import pandas as pd
-import scipy as sp
-from scipy.spatial.distance import mahalanobis
-import copy
-
-# Connect to db
-con = pymysql.connect(host='0.0.0.0', unix_socket='/tmp/mysql.sock', user="root", passwd="123", db='virtass')
-cur = con.cursor(pymysql.cursors.DictCursor)
-
-# Put coefficients of reasons and preferences
-prefList = {"energy": 0, "entertainment": 1, "food": 2, "health": 3, "security": 4, "work": 5}
-usersList = {"adult": 0.6, "young": 0.3, "elder": 0.6}
-
-
-# Function that loads cases and preferences
-def load():
-    with con:
-        cur.execute('SELECT * FROM cases')
-        casesRaw = list(cur.fetchall())
-        cur.execute('SELECT * FROM preferences')
-        prefRaw = list(cur.fetchall())
-        cases = []
-        casesDict = \
-            {"energyI": 0, "entertainmentI": 0, "foodI": 0, "healthI": 0, "securityI": 0, "workI": 0, "usertypeI": 0,
-             "energyO": 0, "entertainmentO": 0, "foodO": 0, "healthO": 0, "securityO": 0, "workO": 0, "usertypeO": 0,
-             "output": 0, "id": 0}
-        cur.execute('SELECT * FROM preferences')
-        prefRaw = list(cur.fetchall())
-
-        # For each element of table is stored into list of training and test sets
-        for k in range(len(casesRaw)):
-            casesDict["output"] = casesRaw[k]["output"]
-            for l in range(len(prefRaw)):
-                if casesRaw[k]["usertypeIN"] == prefRaw[l]["usertype"]:
-                    casesDict[str(casesRaw[k]["reasonIN"] + "I")] = prefRaw[l][str(casesRaw[k]["reasonIN"])]
-                if casesRaw[k]["usertypeOUT"] == prefRaw[l]["usertype"]:
-                    casesDict[str(casesRaw[k]["reasonOUT"] + "O")] = prefRaw[l][str(casesRaw[k]["reasonOUT"])]
-                casesDict["usertypeI"] = usersList[casesRaw[k]["usertypeIN"]]
[…]

### 2018-01-09 CBR/Telepot.py

@@ -1,31 +1,0 @@
-import telepot
-from telepot.loop import MessageLoop
-import time
-import random
-import datetime
-
-token = '425620979:AAHfCI5dbvQLhWaOi-u0w3PmBQWg9hyG_cs'
-bot = telepot.Bot(token)
-
-
-def handle(msg):
-    chat_id = msg['chat']['id']
-    command = msg['text']
-
-    if command == '/gm':
-        file = "./kings.txt"
-        with open(file, 'r') as f:
-            lines = f.readlines()
-            text = lines[-2:]
-        texty = "The last lines of the kings.txt are: \n"
-        for el in text:
-            texty = texty + str(el)
-        bot.sendMessage(chat_id, texty)
-        bot.sendDocument(chat_id, open("./kings.txt", 'rb'))
-
-
-MessageLoop(bot, handle).run_as_thread()
-
-print("I am working...")
-while 1:
-    time.sleep(10)

### 2018-01-09 main.py

@@ -339,4 +339,4 @@ def reasonClassification(username, order, reason):
 # Main flask app
 if __name__ == "__main__":
     # It creates https access by last argument. It is need to be give to web-page permission to microphone
-    app.run(host='0.0.0.0', port=8090)  # ssl_context='adhoc')  # If no need in https, just delete last argument
+    app.run(host='0.0.0.0', port=8090, ssl_context='adhoc')  # If no need in https, just delete last argument

### 2018-01-24 Paper/Paper.tex
Update of Paper

@@
     \begin{abstract}
-        In this work we will examine and develop a Virtual Assistant which is the intelligence system that is used as a control
-        interface of the Smart Home environment in the Farm Side Middlesex University laboratory. Specifically, the system is
-        constructed to give multiple users ability to control devices` statuses by voice or text commands through the dialogue
-        interface. Primarily, the main purpose of the system is to create user friendly interface with conflict resolution based
-        on user cases. As a result, a Case-Based Reasoning algorithm was created with a k-Nearest Neighbor classification algorithm.
+        In this work we will examine and develop a Virtual Assistant that is used as a control
+        interface of the Smart Home environment in the Farm Side Middlesex University laboratory.
+        Specifically, the system is
+        constructed to give multiple users ability to control devices by voice or text commands through the dialogue
+        interface.
+        Primarily, the main purpose of the research is to create user friendly interface with adaptive context aware
+        Case-Based conflict resolution system.
         In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice
         recognition and voice generation instruments were used to implement natural dialogue model of interactions with users.
-        Moreover, the user friendly graphical web interface was developed. Further, a set of randomised double-blinded
-        evaluation tests were established to check procedure of smart home control actions by multiple users.
+        Further, a set of randomised double-blinded
+        evaluation tests were established.
     \end{abstract}
@@
     %
-    Managing a comfortable life could be a challenging task for people with special needs because some of them may need additional
-    assistance to control electronic and electric devices in the living are [1]. The next group of users that probably seek
-    assistance in Activities of Daily Life (ADL) is younger population while adults are away from home [1]. As a result,
-    the Smart Home environments are developed to help users in controlling home and devices states with voice graphical
-    interfaces [10] that are often called Virtual Assistants [1] or monitor behaviours of people
-    with special needs [17] to classify changes in ADL that then alarm or notify relatives, health and care professionals
-    and organizations [9]. Additional finding identified other techniques in the state of art.
+    Managing a comfortable Activities of Daily Life (ADL) could be a challenging task for people with special needs
+    and younger population \cite{9}.
+    As a result,
+    the Smart Home environments are developed to help users in controlling devices \cite{13}
+    that are often called Virtual Assistants \cite{9} or monitor behaviours of people
+    with special needs \cite{3} to classify changes in ADL that then alarm or notify relatives, health and care professionals
+    and organizations \cite{15}.
+    Additional finding identified other techniques in the state of art.
     For example, in Smart Home systems there are Ontology-based platforms that allows to analyze user`s actions and
-    perform context recognition [14] or visual tools for creating personal preferences table of each user based on semantics
-    metadata [11]. As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\
+    perform context recognition \cite{1} or visual tools for creating personal preferences table of each user based on semantics
+    metadata \cite{8}.
+    As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\
+    On the other hand, conflicting orders inside the system by different users can lead to the risks \cite{5}.
     Despite number of
@@
     investigations and development of systems that operates in a conflict resolution between multiple users with different
-    needs and priorities. Some researchers in order to solve this dilemma developed context-aware automation platforms
-    [13, 16] that resolves conflicts between automated devices such as fire alarms and automated door locks.
+    needs and priorities.
+    Some researchers in order to solve this dilemma developed context-aware automation platforms
+    \cite{5,6} that resolves conflicts between automated devices such as fire alarms and automated door locks.
     On the other hand, these solutions resolves conflicts only between automated devices based on priorities of their rules.
     The next group of
-    developers are focused on preference Rule-Based Reasoning (RBR) to resolve conflicts between users [1]. Even through
+    developers are focused on preference Rule-Based Reasoning (RBR) to resolve conflicts between users \cite{9}. Even through
     these systems introduces efficient set of rules, they are not able to handle with adaptation to the new user cases or
     specific out-of-rule situations. \\
-    To sum up
-    state of art, there are number of systems that monitors and adapts to single users, resolves conflicts between devices
-    in single user multi-agent environments and resolves conflicts between users based on if-else rules. On the contrary,
-    there is a lack of the Virtual Assistants with an adaptive conflict resolution systems.\\
     In this research, we propose a Virtual Assistant (VA) system that controls Smart Home environment based on the user inputs via
-    voice and text based dialogue graphical web user interface for multiple users. As a result, we developed number of
-    subsystems to fully implement number of requests. First of all, interaction with the VA has to be user-friendly and
-    natural as a human to human interaction. Second, the system has to be able to control and monitor state of the Smart
-    Home devices. Finally, the VA has to manage to resolve conflicts between multiple users, and adapt to the new user cases.\\
-    To cover all objectives, we introduced and developed the VA with next modules. Firstly, we have developed user friendly
-    graphical interface based on web and cloud technologies to give to user intuitive way of interacting with the VA. For this
-    reason, we used dynamic web framework, cloud voice recognition and generation technologies and animated emotional icons
-    to mimicry natural face emotions in the dialogues. In addition to user friendly interface, we have developed and implemented
-    adaptive natural language classification algorithms based on Artificial Neural Network (ANN) to make the VA understand
-    different variates of the user commands and argumentation sentences, because they are effective algorithms for
-    sentence classification [19]. Therefore, users were able to speak to
-    VA in the way they speak with other human. Secondly, we used Farm Side Middlesex University Smart Home laboratory and
-    Smart Home devices control unit to manage and monitor Smart Home devices. In order that, we have developed and integrated
-    software API to implement communication between Smart Home control unit and VA. The last but not the least, we have
-    introduced and developed a conflict resolution system that used Case-Based Reasoning (CBR) to make a decision about
-    conflict between multiple users. In order to make decision, VA identifies in dialogue form the argumentation of the user
-    in performing an action, analyzes via k-nearest neighbour (kNN) algorithm similarities between
-    this case and previous cases and chooses best-fit case [4,7,15]. In other words, VA asks user to say why he or she wants to change
-    device status if there conflicting instruction from other user and makes decision what to do with device based on users
-    arguments and previous cases. Futhermore, arguments priorities was established by personal user preferences [3] because
-    number of researches shows that the preference-based argumentation increases ability of the systems to meet user
-    expectations [5].\\
-    Furthermore, we have established randomized double-blinded evaluation tests. In order to perform randomized double
-    blinded experiment, we developed scenario creating sub-module. Firstly, it creates random scenario for tester by choosing
-    conflicting device and arguments for tester by using crypto-secure randomise function based on operation system inner
-    clocks. Secondly, it provides such instructions to testers that he or she was
-    asked to provide command and arguments in their own words. As a result, it was hidden from us and testers scenarios till
-    the beginning of the experiment. In addition, testers were asked to fill evaluation form. To conclude, feedback from
-    testers are positive and only weak place of the system is accent recognition task.\\
-    This paper presents Virtual Assistant in the multiple user Smart Home environment. The Virtual Assistant was created
-    to manage and monitor Smart Home environment by dialogue based interaction with users. Different machine learning
-    algorithms and cloud technologies were implemented to meet project objectives. The main focus of the research was to
-    develop adaptive conflict resolution system based on Case-Based Reasoner. The validation tests feedback is positive.
-    The future direction of the work is to implement context-aware system that analyzes user behaviour and reports it as
-    a case to the database of Case-Based Reasoner.\\
-    This paper presents Virtual Assistant in the multiple user Smart Home environment. The architecture of the system is
+    voice and text based dialogue graphical web user interface for multiple users and resolve conflicts in changing environment.\\
+    This paper presents Virtual Assistant in the multiple user Smart Home environment.
+    The architecture of the system is
     described in the Section II. The system algorithms and sequences are described in the Section III. Section IV demonstrates
-    our results and validation. Finally, Section V draws the conclusion and predictions for the future work.
+    our results and validation.
+    Finally, Section V draws the conclusion and predictions for the future work.
     %
@@
     or divided into the groups called components.
-    \subsection{Overall}
+    We have used updated user types and preference system proposed by \cite{9}.
+    Moreover, arguments priorities was established by personal user preferences \cite{11} because
+    number of researches shows that the preference-based argumentation increases ability of the systems to meet user
+    expectations \cite{10}.\\
+    The preferences are reasons why user wants to change the device status.
+    Introducing reason is the way to increase usability of the system through the implicit interpretation of user needs.
+    Context awareness of the system is the key for creating high usability via making the interaction
+    between user and system more natural \cite{7}.\\
+    We have used "Ceteris paribus" preferences binary tree representation.
+    At the moment, CP-nets are most effective qualitative approach for presenting preferences in the strict known
+    environment as the Smart Home \cite{10}.
+    \begin{table}
+        \caption{List of users and preferences}
+        \begin{tabular}{llllll}
+            \hline\noalign{\smallskip}
+            User types & Preferences (positions 0,1,2,3,4,5)\\
+            \noalign{\smallskip}
+            \hline
+            \noalign{\smallskip}
+            Adult (26-69 ages) & Security, Health, Work, Food, Energy, Entertainment\\
+            Elderly (older 70) & Health, Security, Food, Energy, Entertainment, Work\\
+            Young (up to 25 ages) & Security, Work, Entertainment, Health, Food, Energy\\
+            \hline
+        \end{tabular}
+    \end{table}
     The architecture of the system is layered and modular.
@@
     \subsection{Graphical User Interface and Front End}
-    The interface of the system is graphical web interface developed as web site.
-    As a result, Graphical User Interface (GUI) is expressed by 3 functional and Login Pages that are listed below:
-    \begin{enumerate}
-        \item Login Page: Welcome interface - user chooses his or her account.
-        \item Control Page: Dialogue interface - user communicates with system in form of dialogue by voice or text chat,
+    The interface of the system is graphical web interface developed as web site shown in the figure below.
+    Graphical User Interface (GUI) is expressed by 3 functional and Login pages.
+    In the Login Page user chooses account.
+    User communicates with system in form of dialogue by voice or text chat,
     gives orders \footnote{Order is command of the user given to the system.
-For example, turn off the light.} and reasons \footnote{Reason is argument given by the user to the system to justify his/her order.
-For example, turn off the light, because my eyes hurts.}.
-        \item Rules \footnote{Rule is set of instructions given for system to do automatically.
-For example, system is obligated keep kettle turned off from 11:00 till 13:00 everyday because of energy saving issue.}
-        Page: Rules editing interface - user edits list of instructions \footnote{Rules are discussed in the Section III.} given to the system.
-        \item Preferences \footnote{Preference is set of issues that justifies orders of the user to the system.
-Every user type has its own priority level for preferences.} Page: Preferences editing interface - user edits his or her preferences \footnote{Preferences are discussed in the Section III.}.
-    \end{enumerate}
-    Flask Micro Web Framework is used as Front End controlling technology or Back End of the interface, because most of the project is coded by Python 3 language.
+    For example, turn off the light.} and reasons \footnote{Reason is argument given by the user to the system to
+    justify his/her order.
+    For example, turn off the light, because my eyes hurts.} in the Control Page.
+    Rules Page and Preference Page are database table editing pages where user changes rules \footnote{Rule is set of instructions given for system to do automatically.
+    For example, system is obligated keep kettle turned off from 11:00 till 13:00 everyday because of energy saving issue.} and preferences.\\
+    \begin{figure}
+        \includegraphics[width=\textwidth]{mockup.png}
+        \caption[]{Control Page of the web interface}
+    \end{figure}
+    Firstly, header menu with hyperlinks to each page is located on the top of the interface.
+    In the upper left corner of the Control Page there are emotional icon representing facial expressions of the Virtual Assistant
+    and text of the VA answers below it.
+    In addition, usage manual is provided below VA that can be easily closed by clicking "x" button.
+    In the middle of the page, you can find input box with microphone activating and send buttons.
+    In order to explain system, there is instruction block under the input box.
+    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.
     \subsection{Cloud API}
@@
     They are JavaScript Application Programming Interfaces (API) that are used by most of the modern browsers.
-    As a result, the system sends record of the user input to W3C API and it returns text that is the recognition of the record.
+    As a result, the system sends record of the user input to W3C API and it returns recognised text.
     Moreover, the system sends text to the browser of the user in such way that the browser automatically generates it into voice.
-    The modules of the Speech Generation and Speech Recognition are inserted to the Dialogue component with Dilague Manager module.
     \subsection{Core System}
@@
     It consists of Dialogue Manager, Classification Component, Rule-Based Reasoner, Case-Based Reasoner and Device Control Unit.
-    \subsection{Dialogue Manager}
-    Dialogue Manager is one of the central modules of the system.
-    Dialogue Manager receives phrases from the user and classifies it by Classification component and sends it to Rule-Based Reasoner.
-    Based on the data from Rule-Based Reasoner and actions done by the system it sends human readable report or response to user via interface.
-    In addition to Cloud API, Dialogue Manager is part of the Dialogue component that is the subsystem to communicate with user in natural way.
-    Lastly, Dialogue Manager is set of if-else rules and dialogues database developed to pretend human-like speaking.
-    \subsection{Classification Component}
     Classification component is group of two Classification modules that are Order and Reason Classification.
@@
     As a result, they need classification algorithm.\\
-    Text classification is non-trivial complex task that is cannot be solved sequentially or by sequential algorithms artificial neural network systems (ANN) provides the better solution \cite{14}.
-    Backpropagation as an ANS is very useful in recognizing complex patterns and performing nontrivial mapping functions.
-    The figure below represents a simple Feed Forward Neural Network (FNN) diagram.
-    The rounded objects represent the artificial neurons or processing elements of a neural network.
-    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.
-    Also every line of processing elements is a layer of a network.
+    Text classification is non-trivial complex task that is cannot be solved sequentially
+    Artificial neural network systems (ANN) provides the better solution \cite{14}.
+    Backpropagation as an ANN is very useful in recognizing complex patterns and performing nontrivial mapping functions.
+    The figure below represents a Feed Forward Neural Network (FNN) diagram used in the project.
+    The rounded objects represent the artificial neurons.
+    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.\\
     \begin{figure}
@@
     \end{figure}
-    \subsubsection{Topology of the Artificial Neural Network} is consists of Input, Output and Hidden layers.\\
+    Topology of the Artificial Neural Network consists of Input, Output and Hidden layers.\\
     \em Input layer \em consist of input neurons that are binomial representation of the unique stemmed words (stemmed by LancasterStemmer from Natural Language Toolkit library) inside the text that is already cleaned from punctuation and meaningless words like articles.
@@
     These functions are sigmoid linear transformation of the previous layer.
-    As a result, it followed by a squashing nonlinearity
-    While training the ANN (see below) it was concluded that the accuracy of the neural network does not significantly changes between one hidden layer neural network and multiple hidden layer neural network.
-    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was calculated by 1000 iterations of Backpropogation training algorithm with standard training/test set especially created for this experiment.
-    \begin{figure}
-        \includegraphics[width=0.8\textwidth]{HL.png}
-        \caption[]{Iterations of FNN with different Hidden Layer size, where horizontal line is number of neurons and vertical line is delta function percentage}
-    \end{figure}
-    \subsubsection{General Case: Trivial Reason.}
+    As a result, it followed by a squashing nonlinearity.
+    While training the ANN it was concluded that the accuracy of the neural network does not significantly changes between one hidden layer neural network and multiple hidden layer neural network.
+    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was calculated by
+    1000 iterations of Backpropogation training algorithm with standard training/test set especially created for this experiment.\\
     In the next example user typed that he wants to change device status because he needs to finish a project about flu.
     Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.
-    The system normally does not accept any classification lower that 80\% possibility, and if user says something not
-    correlated to the predefined preferences, the system will skip classification and ask again.
+    The system normally does not accept any classification lower that 30\% possibility, and if user says something not
+    correlated to the predefined preferences, the system will skip classification and ask again.\\
     \begin{example}
-        User input is: \em I need to finish my project about flu \em \\
-        System classified it as: \em [['Work', 0.99951473383654765], ['Health', 0.056650409249493161], ['Entertainment', 0.0011293354032656073], ['Energy', 1.4169164768812246e-05], ['Security', 1.238332260956378e-05], ['Food', 3.1674436013529605e-07]] \em
+        User input is: I need to finish my project about flu\\
+        System classified it as: [['Work', 0.99951473383654765], ['Health', 0.056650409249493161], ['Entertainment', 0.0011293354032656073], ['Energy', 1.4169164768812246e-05], ['Security', 1.238332260956378e-05], ['Food', 3.1674436013529605e-07]]
     \end{example}
-    \subsubsection{General Case: Nontrivial Reason.}
-    In the next example user typed "G'ylym janyp turg'an s'yraq" (Kazakh Language: Science is a burning candle).
-    The system did not managed to classify this reason, because the system is tuned only for English.
-    \begin{example}
-        User input is: \em G'ylym janyp turg`an s`yraq \em\\
-        System classified it as: \em [] (Null) \em
-    \end{example}
-    \subsection{Training of FNN}
-    It was used Backpropogation method for artificial neural network weights of the synapses optimisation.
+    It was used Backpropogation method for the synapses optimisation.
     The Backpropagation learning rule based on supervised learning \cite{14}.
-    In order to train neural network, a set of training documents and a specification of the pre-defined categories the documents belong to are required.
+    In order to train neural network, a set of training documents and a specification of the pre-defined categories the
+    documents belong to are required.
     Training and testing sets were created specially for this experiment.
@@
     During training, the connection weights of the neural network are initialized to random values.
-    The training examples in the training set are then presented to the neural network classifier in random order, and the connection weights are adjusted according to the Backpropagation learning rule.
-    This process is repeated until the learning error falls below a predefined tolerance level (99.95\%).
-    Below there is an example of the training of the Reason Classifier.
-    \begin{example}
-        Input matrix: 260x198 Output matrix: 1x6\\
-        delta after 10000 iterations:0.00195103818538\\
-        delta after 20000 iterations:0.00132469839464\\
-        delta after 30000 iterations:0.00105975676227\\
-        delta after 40000 iterations:0.000905619354028\\
-        delta after 50000 iterations:0.000802125845806\\
-        delta after 60000 iterations:0.000726645045015\\
-        delta after 70000 iterations:0.000668536139359\\
-        delta after 80000 iterations:0.000622059862315\\
-        delta after 90000 iterations:0.000583815748815\\
-        delta after 100000 iterations:0.000551645861196\\
-        saved synapses to: ./include/synapses.json\\
-        processing time: 103.20042490959167 seconds\\
-    \end{example}
-    \subsection{Rule-Based Reasoner}
+    The training examples in the training set are then presented to the neural network classifier in random order, and
+    the connection weights are adjusted according to the Backpropagation learning rule.
+    This process is repeated until the learning error falls below a predefined tolerance level (99.95\%).\\
     Rule-Based Reasoner receives data about the user`s order and compares it with rules in the Database and actual status of the devices.
-    Core of the Rule-Based Reasoner is the set of if-else rules:
-    \begin{enumerate}
-        \item If status of device equals to status that user already wants: return similarity response; else: go further.
-        \item If there is conflict between rule and user`s order: send task to Case-Based Reasoner; else: send command to Device COntrol Unit.
-    \end{enumerate}
-    \subsection{Case-Based Reasoner}
-    Case-Based Reasoner works by finding the lowest distance of input case to the cases inside the database.
+    Core of the Rule-Based Reasoner is the set of if-else rules.
+    Firstly, RBR checks the status of the device and compares it with order.
+    Secondly, it checks is there conflict between user command and rule.
+    If there is conflict it executes Case-Based Reasoner (CBR).\\
     CBR is an artificial intelligence approach to determine a similarity amongst a set of cases.
+    CBR is the foundation of the many intelligent systems.
     This method indexes cases from history of the system usage and retrieves best similar case by measurement of distance between the input case and past cases.
     The result of finding best match is stored inside the cases database to update the cases database and adapt old solution to the new variables and environment.
-    CBR is based on a suggestion that the similar cases have similar solution.
-    The decisions in our system is binary (0 for not change device status, 1 for change it).
-    As a result, it is accessible that CBR assumption works in our system.
+    CBR is based on a suggestion that the similar cases have similar solution \cite{7}.\\
     Most of the CBR systems uses k-nearest neighbour algorithm.
@@
     The nearest neighbour algorithm determines the similarity or dissimilarity of a new case with the case base and follows a cyclical process of Retrieve-Reuse-Revise-Retain.
-    In our case inputs to the system are in different system of measurements.
+    In our case inputs to the system are in different systems of measurements.
     Cases in the system are build on preferences and priority of users of the system.
     Both two variables have different basis.
-    As a result, standard Euclidean Distance cannot be used as a distance measurement algorithm.
+    As a result, standard Euclidean Distance cannot be used as a distance measurement algorithm.\\
     It was proposed to use Mahalanobis distance that is the global linear transformation tool of the input spaces of the cases from different classes separated by a large margins.
-    Using of Mahalanobis distance significantly increases kNN accuracy.
-    In addition, there was used a Genetic Algorithm to find best value of Mahalanobis covariance matrix.
-    It is was set nearly 11 quadrillion types of mutations patterns.
-    The covariance matrix was used as genome of each genome in the epoch.
-    As a result, each epoch system chooses best accuracy model and mutates it`s one hundred children with different not significant mutations in the genome.
-    Then the system iterate again while accuracy of the best model (king) will not reach threshold value.
-    \subsection{Device Control Unit}
+    Using of Mahalanobis distance significantly increases kNN accuracy \cite{17}.\\
+    Dialogue Manager is one of the central modules of the system.
+    Dialogue Manager receives phrases from the user and classifies it by Classification component and sends it to Rule-Based Reasoner.
+    Based on the data from Rule-Based Reasoner and actions done by the system it sends human readable report or response to user.\\
     Smart Home environment of the Farm Side Middlesex University is driven by Vera Secure system.
-    In consequence, we developed API to communicate with it.
-    Vera Secure system has own web interface.
-    In order to communicate with it, we sending and receiving GET and POST requests.
-    Special POST requests changes status of the devices, which are kettle and light in our experiment.
-    Next, updating information about device statuses is done by parsing response from special GET request sent to the Vera Secure server.
+    In consequence, we developed API to communicate with it that is represented by Device Control Unit in the architecture diagram.
     \section{Sequences}
@@
     Sequences inside the system are mentioned in this chapter.
-    \subsection{Terminology}
-    We used user types and preference system proposed by \cite{9} .
-    As a result, different group of users were outlined and divided by age.
-    Moreover, we declared updated system of preferences.
-    \begin{table}
-        \caption{List of users and preferences}
-        \begin{tabular}{llllll}
-            \hline\noalign{\smallskip}
-            User types & Preferences (positions 0,1,2,3,4,5)\\
-            \noalign{\smallskip}
-            \hline
-            \noalign{\smallskip}
-            Adult (26-69 ages) & Security, Health, Work, Food, Energy, Entertainment\\
-            Elderly (older 70) & Health, Security, Food, Energy, Entertainment, Work\\
-            Young (up to 25 ages) & Security, Work, Entertainment, Health, Food, Energy\\
-            \hline
-        \end{tabular}
-    \end{table}
-
-    \subsection{Regular Case}
-    \subsection{Conflicting Case}
+    Sequence diagram of the system can be found in figure below.
+    It shows three main scenarios\footnote{Scenario - set of similar cases} inside the system.\\
+    \begin{figure}
+        \includegraphics[width=\textwidth]{UML.png}
+        \caption[]{UML Sequence diagram of the system}
+    \end{figure}
+    In order to describe system lifelines, there is explanation of the scenarios.
+    First of all, the user sends command to the system (1.1) that is analysed by Dialogue Component (1.2) via Classification ANN (1.3, 1.4).
+    Next, system sends classified order to the RBR (1.5) and checks it`s context (1.6 - 1.9).
+    If there is no conflict, it changes device status (1.10, 1.11) and answers to the user (1.12 - 1.14).
+    Else, it executes Conflict Resolution Scenario by Case-Based Reasoner (2.1).\\
+    Next, it informs the user about conflict (2.2 - 2.4) and wait command.
+    If the user cancels command (2.5, 2.6), it aborts Conflict Resolution loop.
+    Else, the system asks for argumentation (2.7, 2.8) from user (2.9, 2.10) and classifies it (2.11, 2.12).
+    After collection of data (2.13) CBR reads old cases (2.14, 2.15) and makes a decision (2.16).\\
+    In the settings pages the user changes database (3.1 - 3.4).
     \section{Results and Validation}
     %
-    \section{Conclution}
-    \section{References}
+    To evaluate the system we have constructed randomised double-blind experiment.
+    In order to perform randomized double
+    blinded experiment, we developed scenario creating sub-module.
+    Firstly, it creates random scenario for tester by choosing
+    conflicting device and reasons for tester by using crypto-secure randomise function based on operation system inner
+    clocks.
+    Secondly, it provides such instructions to testers that he or she was
+    asked to provide command and arguments in their own words.
+    As a result, scenarios were hidden from us and testers till
+    the beginning of the experiment.\\
+    In addition, thirteen testers were asked to fill evaluation form.
+    In the evaluation form testers were asked to answers questions with quantitative form, where 0 is very badly and 4 is very good, about Speech recognition,
+    classification, conflict resolution, total idea, interface design, interaction with VA and user friendliness.
+    Furthermore, they were provided with additional text box under each question to justify their answers if they though
+    that they need to be justified and one more question about what they would include or change in the system.\\
+    The majority of the responses were positive \footnote{83 of 91 quantitative answers are positive, 5 neutral and 3 negative.}
+    and the average of the all answers are higher the "Good" level (3 and more) except "Conflict Resolution" question, which
+    has 2.9 average value with 1.2 standard deviation amount.
+    The basic quantitative analysis of the answers are shown in the figure below.\\
+    \begin{figure}
+        \includegraphics[width=\textwidth]{eval.png}
+        \caption[]{Quantitative analysis of the answers}
+    \end{figure}
+    The question about conflict resolution quality was the most hard for the system, because it has two negative answers.
+    Firstly, there was disagreement about priorities policy of the system and the general view of the user.
+    The tester did not agree that the adult has higher priority with entertainment issue versus younger with work issue.
+    The second case was unique and new to the CBR, and it did not managed to give appropriate output.
+    Analysis of the system logs and simulation of the case gave us better understanding of the system fault.
+    As a result, there is a list of possible cause effects and ways to solve them:\\
+    \begin{enumerate}
+        \item Lack of training data: create more training cases and store them into Databases.
+        \item Ineffective distance measurement algorithm: replace k-Nearest Neighbor algorithm with Artificial Neural Network or other machine learning algorithm.
+Combination of heuristic algorithms gives higher results than separately \cite{12}.
+        \item Ineffective input matrix: replace input variables by new system that will take into account difference between reasons.
+    \end{enumerate}
+    \section{Conclusion}
+    This paper presents Virtual Assistant in the multiple user Smart Home environment.
+    The Virtual Assistant was created
+    to manage and monitor Smart Home environment by dialogue based interaction with users.
+    Different machine learning
+    algorithms and cloud technologies were implemented to meet project objectives.
+    The main focus of the research was to
+    develop adaptive context aware conflict resolution system based on Case-Based Reasoner.
+    The validation tests feedback is positive.
+    The future direction of the work is to implement context-aware system that analyzes user behaviour and reports it as
+    a case to the database of Case-Based Reasoner.
+    In order to change paradigm from technology centered perspective to human centered perspective,
+    it is significant to introduce behaviour adapting sub-system \cite{2}.\\
+    In addition, it is recommended to implement machine learning algorithms to measure distances between cases to
+    increase accuracy of the Case-Based Reasoner.\\
+    All the materials and sources of the system can be found in the GitHub repository of the project \footnote{https://github.com/BiggyBaron/VirtualAssistant}.
+    Furthermore, there is well structured and full observing documentation is available on Wiki page of the system \footnote{https://github.com/BiggyBaron/VirtualAssistant/wiki}.
     \begin{thebibliography}{1}
@@
 14, 274-283 (2010).
-
-        \bibitem {4}
-        Göynügür, E., Bernardini, S., de Mel, G., Talamadupula, K., Şensoy, M.: Policy Conflict Resolution in IoT via Planning. Advances in Artificial Intelligence. 169-175 (2017).
 
@@
 
-        \bibitem {16}
-        Siolas, G., Caridakis, G., Mylonas, P., Kollias, S., Stafylopatis, A.: Context-Aware User Modeling and Semantic Interoperability in Smart Home Environments.
-2013 8th International Workshop on Semantic and Social Media Adaptation and Personalization.
-(2013).
-
         \bibitem {17}

### 2018-01-24 CBR/CBR.py

@@ -6,6 +6,7 @@ import pandas as pd
 import scipy as sp
 from scipy.spatial.distance import mahalanobis
 import copy
+from random import shuffle
 
 # Connect to db
 con = pymysql.connect(host='0.0.0.0', unix_socket='/tmp/mysql.sock', user="root", passwd="123", db='virtass')
@@ -13,7 +14,7 @@ cur = con.cursor(pymysql.cursors.DictCursor)
 
 # Put coefficients of reasons and preferences
 prefList = {"energy": 0, "entertainment": 1, "food": 2, "health": 3, "security": 4, "work": 5}
-usersList = {"adult": 3, "young": 2, "elder": 1}
+usersList = {"adult": 3, "young": 1, "elder": 2}
 
 
 # Function that loads cases and preferences
@@ -116,4 +117,3 @@ def main(usertypein, usertypeout, reasonin, reasonout):
             'id': 0}
     # Returning result
     return Calculate(Mahalanobis, test)
-

### 2018-01-26 Paper/Paper.tex
Update of Paper

@@
 \usepackage{graphicx}
-\graphicspath{ {Images/} }
+\graphicspath{{Images/}}
 %
@@
     Multi-User Smart Home Environment}
-    \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Jose Quinde Li Say Tan \inst{2} \and Kenzhegali Nurgaliyev \inst{1}}
+    \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Quinde \inst{2} \inst{3} \and Kenzhegali Nurgaliyev \inst{1}}
     \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@nu.edu.kz}
-    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{N.X.Khan,J.Augusto,MQ093}@live.mdx.ac.uk}}
+    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{N.X.Khan,J.Augusto,MQ093}@live.mdx.ac.uk}
+    \and Department of Industrial and Systems Engineering, Universidad de Piura, Av. Ramon Mujica 131, Urb. San Eduardo, Piura, Peru\\
+    \email{mario.quinde@udep.pe}}
     \maketitle
@@
         interface.
-        Primarily, the main purpose of the research is to create user friendly interface with adaptive context aware
+        The main purpose of the research is to create user friendly interface with adaptive context aware
         Case-Based conflict resolution system.
@@
     Some researchers in order to solve this dilemma developed context-aware automation platforms
-    \cite{5,6} that resolves conflicts between automated devices such as fire alarms and automated door locks.
-    On the other hand, these solutions resolves conflicts only between automated devices based on priorities of their rules.
+    \cite{5,6} that resolves conflicts between automated devices.
+    These solutions resolves conflicts only between automated devices based on priorities.
     The next group of
-    developers are focused on preference Rule-Based Reasoning (RBR) to resolve conflicts between users \cite{9}. Even through
-    these systems introduces efficient set of rules, they are not able to handle with adaptation to the new user cases or
-    specific out-of-rule situations. \\
+    developers are focused on preference Rule-Based Reasoning (RBR) \cite{9}.
+    Even through
+    these systems introduce efficient set of rules, they are not able to handle with adaptation. \\
     In this research, we propose a Virtual Assistant (VA) system that controls Smart Home environment based on the user inputs via
-    voice and text based dialogue graphical web user interface for multiple users and resolve conflicts in changing environment.\\
-    This paper presents Virtual Assistant in the multiple user Smart Home environment.
+    voice and text based dialogue graphical web user interface for multiple users and resolve conflicts in changing environment.
     The architecture of the system is
@@
     %
-    Technical details of the system are given in this section.
-    It consider architecture diagram of the system and explanation of all functional units called modules each
+    Technical details of the system
+    consider architecture diagram of the system and explanation of all functional units called modules
     or divided into the groups called components.
     We have used updated user types and preference system proposed by \cite{9}.
-    Moreover, arguments priorities was established by personal user preferences \cite{11} because
+    Moreover, argument priorities were established by personal user preferences \cite{11} because
     number of researches shows that the preference-based argumentation increases ability of the systems to meet user
@@
     Context awareness of the system is the key for creating high usability via making the interaction
-    between user and system more natural \cite{7}.\\
+    between user and system more natural \cite{7}.
     We have used "Ceteris paribus" preferences binary tree representation.
     At the moment, CP-nets are most effective qualitative approach for presenting preferences in the strict known
-    environment as the Smart Home \cite{10}.
+    environment as the Smart Home \cite{10}.\\
     \begin{table}
@@
     The architecture of the system is layered and modular.
-    As a result, each functional part (module) of the system is designed to execute complete task and some of them are
-    divided into components.
+    As a result, each functional part (module) of the system is designed to execute complete task.
     The component is group of modules that performs complex task that consists of a number of simple tasks.
@@
     In addition, in order to give better understanding of the system, the architecture is divided into layers.
-    Layer is functional components of the system that sequentially divides it into hierarchical groups that
-    communicates only with layer above or layer below except Database layer.
-    For example, Cloud API layer is consists of Speech Generation and Speech Recognition that communicate only with
-    Front End layer and Core layer.\\
+    Layer is functional level of the system that sequentially divides it into hierarchical groups that
+    communicates only with layer above or layer below except Database layer.\\
     Layer is demonstrated as white rectangle with grey icon and name in it.
     Web pages of the web interface is demonstrated as white colored box with blue drawing and text in it.
-    Hexagonal icon with white image inside colored blue and text below is module of the system.
+    Blue hexagonal icon with white image inside and text below is module of the system.
     White quadrilateral with grey illustration of device and it`s name underneath is icon of electronic device driven
@@
     Colored rectangle with text in the bottom right corner is illustration of components.
-    All communication inside the system is demonstrated as arrows in the Fig.1.
+    All communications inside the system is demonstrated as arrows in the Fig.1.
     \footnote{Communication types and lifelines of the system is described in the Section III.}
@@
     \end{figure}
-    \subsection{Graphical User Interface and Front End}
+    \subsection{Graphical User Interface, Front End and Cloud API}
     The interface of the system is graphical web interface developed as web site shown in the figure below.
-    Graphical User Interface (GUI) is expressed by 3 functional and Login pages.
-    In the Login Page user chooses account.
-    User communicates with system in form of dialogue by voice or text chat,
-    gives orders \footnote{Order is command of the user given to the system.
-    For example, turn off the light.} and reasons \footnote{Reason is argument given by the user to the system to
-    justify his/her order.
-    For example, turn off the light, because my eyes hurts.} in the Control Page.
-    Rules Page and Preference Page are database table editing pages where user changes rules \footnote{Rule is set of instructions given for system to do automatically.
-    For example, system is obligated keep kettle turned off from 11:00 till 13:00 everyday because of energy saving issue.} and preferences.\\
+    Graphical User Interface (GUI) is expressed by 3 functional and one login pages.\\
     \begin{figure}
@@
     In order to explain system, there is instruction block under the input box.
-    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.
-    \subsection{Cloud API}
-    The function units of the Speech Generation and Speech Recognition were established via W3C Web Speech API \footnote{More information on https://w3c.github.io/speech-api/speechapi.html.}.
+    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.\\
+    The function units of the Speech Generation and Speech Recognition were established via W3C Web Speech API.
     They are JavaScript Application Programming Interfaces (API) that are used by most of the modern browsers.
@@
     \subsection{Core System}
-    Core System is main functional layer of the system.
-    Consequently, functions as decision-making, dialogue compilation, text classification and device controlling are all executed in the modules inside the Core System layer.
-    It consists of Dialogue Manager, Classification Component, Rule-Based Reasoner, Case-Based Reasoner and Device Control Unit.
+    Core System is main functional layer.
+    Consequently, functions as decision-making, dialogue compilation, text classification and device controlling are all executed in the Core System.
+    It consists of Dialogue Manager, Classification Component, Rule-Based Reasoner, Case-Based Reasoner and Device Control Unit.\\
     Classification component is group of two Classification modules that are Order and Reason Classification.
     Their function is to classify orders and reason from user input raw data.
-    As a result, they need classification algorithm.\\
+    As a result, they need classification algorithm.
     Text classification is non-trivial complex task that is cannot be solved sequentially
@@
     Topology of the Artificial Neural Network consists of Input, Output and Hidden layers.\\
-    \em Input layer \em consist of input neurons that are binomial representation of the unique stemmed words (stemmed by LancasterStemmer from Natural Language Toolkit library) inside the text that is already cleaned from punctuation and meaningless words like articles.
-    In a text document a word may exist in a different morphological variants.
-    For example the word “love” may also exist in other morphological variants such as “loving”, “loved”.
-    While these morphological variants are different word forms, that represent same concept.
+    \em Input layer \em consist of input neurons that are binomial representation of the unique stemmed words inside the text that is already cleaned from punctuation and meaningless words like articles.
+    While morphological variants are different word forms, they represent same concept.
     In text categorization and other similar tasks it is desirable to combine these morphological variants of the same word into one canonical form and represent it like vector that is called stemmed version.\\
-    \em Output layer \em gives vector of possibilities that the text is inside of classes \footnote{Class is the group of reasons for Reason Classification and group of orders for Order Classification.}.
+    \em Output layer \em gives vector of possibilities that the text is inside of classes.
     The most possible class is the classification answer of the neural network.\\
@@
     As a result, it followed by a squashing nonlinearity.
-    While training the ANN it was concluded that the accuracy of the neural network does not significantly changes between one hidden layer neural network and multiple hidden layer neural network.
-    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was calculated by
-    1000 iterations of Backpropogation training algorithm with standard training/test set especially created for this experiment.\\
+    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was found by
+    1000 iterations of Backpropogation training algorithm.\\
     In the next example user typed that he wants to change device status because he needs to finish a project about flu.
-    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.
-    The system normally does not accept any classification lower that 30\% possibility, and if user says something not
-    correlated to the predefined preferences, the system will skip classification and ask again.\\
+    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.\\
     \begin{example}
         User input is: I need to finish my project about flu\\
-        System classified it as: [['Work', 0.99951473383654765], ['Health', 0.056650409249493161], ['Entertainment', 0.0011293354032656073], ['Energy', 1.4169164768812246e-05], ['Security', 1.238332260956378e-05], ['Food', 3.1674436013529605e-07]]
+        System classified it as: 'Work': 0.999, 'Health': 0.0566
     \end{example}
-    It was used Backpropogation method for the synapses optimisation.
-    The Backpropagation learning rule based on supervised learning \cite{14}.
+    The Backpropagation learning rule based on supervised learning was used \cite{14}.
     In order to train neural network, a set of training documents and a specification of the pre-defined categories the
     documents belong to are required.
-    Training and testing sets were created specially for this experiment.
-    There were used common English phrases and their synonyms to create set of sentences and their class.
-    During training, the connection weights of the neural network are initialized to random values.
-    The training examples in the training set are then presented to the neural network classifier in random order, and
-    the connection weights are adjusted according to the Backpropagation learning rule.
-    This process is repeated until the learning error falls below a predefined tolerance level (99.95\%).\\
+    Training and testing sets were created specially for this experiment.\\
     Rule-Based Reasoner receives data about the user`s order and compares it with rules in the Database and actual status of the devices.
@@
     Secondly, it checks is there conflict between user command and rule.
-    If there is conflict it executes Case-Based Reasoner (CBR).\\
+    If there is a conflict it executes Case-Based Reasoner (CBR).\\
     CBR is an artificial intelligence approach to determine a similarity amongst a set of cases.
@@
     Using of Mahalanobis distance significantly increases kNN accuracy \cite{17}.\\
-    Dialogue Manager is one of the central modules of the system.
-    Dialogue Manager receives phrases from the user and classifies it by Classification component and sends it to Rule-Based Reasoner.
-    Based on the data from Rule-Based Reasoner and actions done by the system it sends human readable report or response to user.\\
-    Smart Home environment of the Farm Side Middlesex University is driven by Vera Secure system.
-    In consequence, we developed API to communicate with it that is represented by Device Control Unit in the architecture diagram.
     \section{Sequences}
@@
     Sequence diagram of the system can be found in figure below.
-    It shows three main scenarios\footnote{Scenario - set of similar cases} inside the system.\\
+    It shows two main scenarios inside the system.\\
     \begin{figure}
-        \includegraphics[width=\textwidth]{UML.png}
+        \includegraphics[width=0.7\textwidth]{UML.png}
         \caption[]{UML Sequence diagram of the system}
     \end{figure}
-    In order to describe system lifelines, there is explanation of the scenarios.
     First of all, the user sends command to the system (1.1) that is analysed by Dialogue Component (1.2) via Classification ANN (1.3, 1.4).
@@
     After collection of data (2.13) CBR reads old cases (2.14, 2.15) and makes a decision (2.16).\\
-    In the settings pages the user changes database (3.1 - 3.4).
     \section{Results and Validation}
     %
-    To evaluate the system we have constructed randomised double-blind experiment.
     In order to perform randomized double
@@
     clocks.
-    Secondly, it provides such instructions to testers that he or she was
-    asked to provide command and arguments in their own words.
+    Secondly, it provides such instructions to testers where he or she was
+    asked to provide commands in their own words.
     As a result, scenarios were hidden from us and testers till
@@
     classification, conflict resolution, total idea, interface design, interaction with VA and user friendliness.
-    Furthermore, they were provided with additional text box under each question to justify their answers if they though
-    that they need to be justified and one more question about what they would include or change in the system.\\
+    Furthermore, they were provided with additional text box under each question to justify their answers.\\
     The majority of the responses were positive \footnote{83 of 91 quantitative answers are positive, 5 neutral and 3 negative.}
     and the average of the all answers are higher the "Good" level (3 and more) except "Conflict Resolution" question, which
-    has 2.9 average value with 1.2 standard deviation amount.
-    The basic quantitative analysis of the answers are shown in the figure below.\\
-    \begin{figure}
-        \includegraphics[width=\textwidth]{eval.png}
-        \caption[]{Quantitative analysis of the answers}
-    \end{figure}
-    The question about conflict resolution quality was the most hard for the system, because it has two negative answers.
+    has 2.9 average value with 1.2 standard deviation amount.\\
+    The question about conflict resolution quality was the most complicated for the system, because it has two negative answers.
     Firstly, there was disagreement about priorities policy of the system and the general view of the user.
@@
     Analysis of the system logs and simulation of the case gave us better understanding of the system fault.
-    As a result, there is a list of possible cause effects and ways to solve them:\\
-    \begin{enumerate}
-        \item Lack of training data: create more training cases and store them into Databases.
-        \item Ineffective distance measurement algorithm: replace k-Nearest Neighbor algorithm with Artificial Neural Network or other machine learning algorithm.
-Combination of heuristic algorithms gives higher results than separately \cite{12}.
-        \item Ineffective input matrix: replace input variables by new system that will take into account difference between reasons.
-    \end{enumerate}
+    As a result, there is a list of possible cause effects and ways to solve them.
+    Firstly, lack of training data can be solved by creating more training cases and store them into Databases.
+    Second, changing the input matrix formulation might be solution.\\
     \section{Conclusion}
@@
     develop adaptive context aware conflict resolution system based on Case-Based Reasoner.
-    The validation tests feedback is positive.
+    The validation tests feedback is positive.\\
     The future direction of the work is to implement context-aware system that analyzes user behaviour and reports it as
@@
     In order to change paradigm from technology centered perspective to human centered perspective,
-    it is significant to introduce behaviour adapting sub-system \cite{2}.\\
+    it is significant to introduce behaviour adapting sub-system \cite{2}.
     In addition, it is recommended to implement machine learning algorithms to measure distances between cases to
@@
     All the materials and sources of the system can be found in the GitHub repository of the project \footnote{https://github.com/BiggyBaron/VirtualAssistant}.
-    Furthermore, there is well structured and full observing documentation is available on Wiki page of the system \footnote{https://github.com/BiggyBaron/VirtualAssistant/wiki}.
     \begin{thebibliography}{1}

### 2018-01-30 Paper/Paper.tex
удалено:       Paper/Images/CBR.png 	удалено:       Paper/Images/CBR1.png 	удалено:       Paper/Images/CBRefficiencychart.png 	удалено:       Paper/Images/DM.png 	удалено:       Paper/Images/Evaluation Tests.png 	удалено:       Paper/Images/FNN.png 	удалено:       Paper/Images/GA.png 	удалено:       Paper/Images/HL.png 	удалено:       Paper/Images/Instructions.jpg 	удалено:       Paper/Images/RBR.png 	удалено:       Paper/Images/arch-legend.png 	изменено:      Paper/Images/arch.png 	удалено:       Paper/Images/chartGA.png 	удалено:       Paper/Images/mahalanobis.png 	удалено:       Paper/Image

@@
     \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Quinde \inst{2} \inst{3} \and Kenzhegali Nurgaliyev \inst{1}}
-    \institute{Department of Information Technology, Kazakh University of Technology and Business, Kayim Muhamedhanov 37A, Astana 010000, Kazakhstan \\ \email{{bospan,knurgaliev}@nu.edu.kz}
-    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{N.X.Khan,J.Augusto,MQ093}@live.mdx.ac.uk}
-    \and Department of Industrial and Systems Engineering, Universidad de Piura, Av. Ramon Mujica 131, Urb. San Eduardo, Piura, Peru\\
+    \institute{Dept. of Information Technology, Kazakh University of Technology and Business, Kazakhstan \\ \email{{bospan,knurgaliev}@nu.edu.kz}
+    \and Dept. of Computer Science, Middlesex University, UK \\ \email{{{N.X.Khan,J.Augusto}@mdx.ac.uk}, {MQ093@live.mdx.ac.uk}}
+    \and Dept. of Industrial and Systems Engineering, Universidad de Piura, Peru\\
     \email{mario.quinde@udep.pe}}
@@
         In this work we will examine and develop a Virtual Assistant that is used as a control
-        interface of the Smart Home environment in the Farm Side Middlesex University laboratory.
+        interface of the Smart Home environment in the Middlesex University laboratory.
         Specifically, the system is
@@
         Case-Based conflict resolution system.
-        In addition, Feed-Forward Artificial Neural Networks were used to classify user inputs, voice
-        recognition and voice generation instruments were used to implement natural dialogue model of interactions with users.
-        Further, a set of randomised double-blinded
+        In addition, Artificial Neural Networks were used to classify user inputs to implement natural dialogue.
+        Further, a set of random double-blinded
         evaluation tests were established.
@@
     %
+
     Managing a comfortable Activities of Daily Life (ADL) could be a challenging task for people with special needs
@@
     metadata \cite{8}.
-    As a consequence, majority of the researches is aimed to develop systems that helps alone living users.\\
+    As a consequence, majority of the researches is aimed to develop systems that helps alone living users.
     On the other hand, conflicting orders inside the system by different users can lead to the risks \cite{5}.
@@
     \cite{5,6} that resolves conflicts between automated devices.
-    These solutions resolves conflicts only between automated devices based on priorities.
-    The next group of
-    developers are focused on preference Rule-Based Reasoning (RBR) \cite{9}.
+    The next group is focused on preference Rule-Based Reasoning (RBR) \cite{9}.
     Even through
@@
     number of researches shows that the preference-based argumentation increases ability of the systems to meet user
-    expectations \cite{10}.\\
+    expectations \cite{10}.
     The preferences are reasons why user wants to change the device status.
@@
     At the moment, CP-nets are most effective qualitative approach for presenting preferences in the strict known
-    environment as the Smart Home \cite{10}.\\
+    environment as the Smart Home \cite{10}.
     \begin{table}
@@
     As a result, each functional part (module) of the system is designed to execute complete task.
-    The component is group of modules that performs complex task that consists of a number of simple tasks.
-    For example, Order Classification and Reason Classification modules are grouped to Classification component.\\
+    The component is a group of modules that performs complex task that consists of a number of simple tasks.
     In addition, in order to give better understanding of the system, the architecture is divided into layers.
@@
     communicates only with layer above or layer below except Database layer.\\
-    Layer is demonstrated as white rectangle with grey icon and name in it.
+    Layer is a white rectangle with grey icon and name in it.
     Web pages of the web interface is demonstrated as white colored box with blue drawing and text in it.
@@
     All communications inside the system is demonstrated as arrows in the Fig.1.
-    \footnote{Communication types and lifelines of the system is described in the Section III.}
-    \begin{figure}
-        \includegraphics[width=\textwidth]{arch.png}
+    \begin{figure} \centering
+        \includegraphics[trim=left botm right top, width=\textwidth, clip]{arch.png}
         \caption[]{Architecture diagram of the system}
@@
     The interface of the system is graphical web interface developed as web site shown in the figure below.
-    Graphical User Interface (GUI) is expressed by 3 functional and one login pages.\\
-    \begin{figure}
-        \includegraphics[width=\textwidth]{mockup.png}
-        \caption[]{Control Page of the web interface}
-    \end{figure}
+    Graphical User Interface (GUI) is expressed by 3 functional and one login pages.
     Firstly, header menu with hyperlinks to each page is located on the top of the interface.
@@
     In order to explain system, there is instruction block under the input box.
-    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.\\
-    The function units of the Speech Generation and Speech Recognition were established via W3C Web Speech API.
-    They are JavaScript Application Programming Interfaces (API) that are used by most of the modern browsers.
-    As a result, the system sends record of the user input to W3C API and it returns recognised text.
-    Moreover, the system sends text to the browser of the user in such way that the browser automatically generates it into voice.
+    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.
+    \begin{figure} \centering \centering
+        \includegraphics[trim=left botm right top, width=\textwidth, clip]{mockup.png}
+        \caption[]{Control Page of the web interface}
+    \end{figure}
+
     \subsection{Core System}
@@
     The rounded objects represent the artificial neurons.
-    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.\\
-    \begin{figure}
-        \includegraphics[width=\textwidth]{ANN.png}
+    The directed lines that are connecting the neurons are called weights that are the multiplication coefficients for input signal.
+    \begin{figure} \centering \centering
+        \includegraphics[trim=left botm right top, width=\textwidth, clip]{ANN.png}
         \caption[]{Classification Neural Network Topology}
     \end{figure}
-    Topology of the Artificial Neural Network consists of Input, Output and Hidden layers.\\
+    Topology of the Artificial Neural Network consists of Input, Output and Hidden layers.
     \em Input layer \em consist of input neurons that are binomial representation of the unique stemmed words inside the text that is already cleaned from punctuation and meaningless words like articles.
     While morphological variants are different word forms, they represent same concept.
-    In text categorization and other similar tasks it is desirable to combine these morphological variants of the same word into one canonical form and represent it like vector that is called stemmed version.\\
+    In text categorization and other similar tasks it is desirable to combine these morphological variants of the same word into one canonical form and represent it like vector that is called stemmed version.
     \em Output layer \em gives vector of possibilities that the text is inside of classes.
-    The most possible class is the classification answer of the neural network.\\
+    The most possible class is the classification answer of the neural network.
     \em Hidden layer \em is the regression function of FNN, or layer between input and output layers.
@@
     The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was found by
-    1000 iterations of Backpropogation training algorithm.\\
+    1000 iterations of Backpropogation training algorithm  \cite{14}.\\
     In the next example user typed that he wants to change device status because he needs to finish a project about flu.
-    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.\\
+    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.
     \begin{example}
@@
     \end{example}
-    The Backpropagation learning rule based on supervised learning was used \cite{14}.
-    In order to train neural network, a set of training documents and a specification of the pre-defined categories the
-    documents belong to are required.
-    Training and testing sets were created specially for this experiment.\\
-    Rule-Based Reasoner receives data about the user`s order and compares it with rules in the Database and actual status of the devices.
-    Core of the Rule-Based Reasoner is the set of if-else rules.
-    Firstly, RBR checks the status of the device and compares it with order.
-    Secondly, it checks is there conflict between user command and rule.
-    If there is a conflict it executes Case-Based Reasoner (CBR).\\
-    CBR is an artificial intelligence approach to determine a similarity amongst a set of cases.
-    CBR is the foundation of the many intelligent systems.
+    Rule-Based Reasoner (RBR) receives data about the user`s order and compares it with rules in the Database and actual status of the devices.
+    If there is a conflict it executes Case-Based Reasoner (CBR).
+    CBR is an artificial intelligence approach to determine a similarity among a set of cases.
     This method indexes cases from history of the system usage and retrieves best similar case by measurement of distance between the input case and past cases.
     The result of finding best match is stored inside the cases database to update the cases database and adapt old solution to the new variables and environment.
-    CBR is based on a suggestion that the similar cases have similar solution \cite{7}.\\
-    Most of the CBR systems uses k-nearest neighbour algorithm.
-    The accuracy of this classification algorithm seriously depends on the metrics or system of measurement used to compute distances between different cases.
-    The nearest neighbour algorithm determines the similarity or dissimilarity of a new case with the case base and follows a cyclical process of Retrieve-Reuse-Revise-Retain.
-    In our case inputs to the system are in different systems of measurements.
-    Cases in the system are build on preferences and priority of users of the system.
-    Both two variables have different basis.
-    As a result, standard Euclidean Distance cannot be used as a distance measurement algorithm.\\
+    CBR is based on a suggestion that the similar cases have similar solution \cite{7}.
     It was proposed to use Mahalanobis distance that is the global linear transformation tool of the input spaces of the cases from different classes separated by a large margins.
-    Using of Mahalanobis distance significantly increases kNN accuracy \cite{17}.\\
+    Using of Mahalanobis distance significantly increases kNN accuracy \cite{17}.
     \section{Sequences}
@@
     It shows two main scenarios inside the system.\\
-    \begin{figure}
-        \includegraphics[width=0.7\textwidth]{UML.png}
+    \begin{figure} \centering
+        \includegraphics[trim=left botm right top, width=0.7\textwidth, clip]{UML.png}
         \caption[]{UML Sequence diagram of the system}
@@
     First of all, the user sends command to the system (1.1) that is analysed by Dialogue Component (1.2) via Classification ANN (1.3, 1.4).
-    Next, system sends classified order to the RBR (1.5) and checks it`s context (1.6 - 1.9).
+    System sends classified order to the RBR (1.5) and checks it`s context (1.6 - 1.9).
     If there is no conflict, it changes device status (1.10, 1.11) and answers to the user (1.12 - 1.14).
     Else, it executes Conflict Resolution Scenario by Case-Based Reasoner (2.1).\\
-    Next, it informs the user about conflict (2.2 - 2.4) and wait command.
+    Conflict Resolution scenario starts with informing the user about a conflict (2.2 - 2.4).
     If the user cancels command (2.5, 2.6), it aborts Conflict Resolution loop.
     Else, the system asks for argumentation (2.7, 2.8) from user (2.9, 2.10) and classifies it (2.11, 2.12).
-    After collection of data (2.13) CBR reads old cases (2.14, 2.15) and makes a decision (2.16).\\
+    After collection of data (2.13) CBR reads old cases (2.14, 2.15) and makes a decision (2.16).
     \section{Results and Validation}
@@
     classification, conflict resolution, total idea, interface design, interaction with VA and user friendliness.
-    Furthermore, they were provided with additional text box under each question to justify their answers.\\
-    The majority of the responses were positive \footnote{83 of 91 quantitative answers are positive, 5 neutral and 3 negative.}
-    and the average of the all answers are higher the "Good" level (3 and more) except "Conflict Resolution" question, which
+    The majority of the responses were positive, where 83 of 91 quantitative answers are positive, 5 neutral and 3 negative.
+    An average of the all answers are higher then the "Good" level (3 and more) except "Conflict Resolution" question, which
     has 2.9 average value with 1.2 standard deviation amount.\\
@@
     Firstly, lack of training data can be solved by creating more training cases and store them into Databases.
-    Second, changing the input matrix formulation might be solution.\\
+    Second, changing the input matrix might be solution.
     \section{Conclusion}
@@
     The main focus of the research was to
-    develop adaptive context aware conflict resolution system based on Case-Based Reasoner.
-    The validation tests feedback is positive.\\
+    develop adaptive context aware conflict resolution system based on CBR.
+    The validation tests are positive.\\
     The future direction of the work is to implement context-aware system that analyzes user behaviour and reports it as
-    a case to the database of Case-Based Reasoner.
+    a case to the database of CBR.
     In order to change paradigm from technology centered perspective to human centered perspective,
@@
     In addition, it is recommended to implement machine learning algorithms to measure distances between cases to
-    increase accuracy of the Case-Based Reasoner.\\
+    increase accuracy.\\
     All the materials and sources of the system can be found in the GitHub repository of the project \footnote{https://github.com/BiggyBaron/VirtualAssistant}.
@@
         Hadj, R., Hamon, C., Chollet, S., Vega, G., Lalanda, P.: Context-based conflict management in pervasive platforms.
-2017 IEEE International Conference on Pervasive Computing and Communications Workshops (PerCom Workshops).
+2017 IEEE Int.
+Conf.
+on Pervasive Computing and Communications Workshops (PerCom Workshops).
 (2017).
@@
         \bibitem {6}
-        Kabir, M., Hoque, M., Seo, H., Yang, S.: Machine Learning Based Adaptive Context-Aware System for Smart Home Environment, https://pdfs.semanticscholar.org/8cf5/fe5062727744f5429bb34d9c0bd24f439ee6.pdf.
+        Kabir, M., Hoque, M., Seo, H., Yang, S.: Machine Learning Based Adaptive Context-Aware System for Smart Home Environment.
 
@@
         Mayer, S., Inhelder, N., Verborgh, R., Van de Walle, R., Mattern, F.: Configuration of smart environments made simple: Combining visual modeling with semantic metadata and reasoning.
-2014 International Conference on the Internet of Things (IOT).
+2014 Int.
+Conf.
+on the Internet of Things (IOT).
 (2014).
@@
         Nurgaliyev, K., Mauro, D., Khan, N., Augusto, J.: Improved Multi-user Interaction in a Smart Environment Through a Preference-Based Conflict Resolution Virtual Assistant.
-2017 International Conference on Intelligent Environments (IE).
+2017 Int.
+Conf.
+on Intelligent Environments (IE).
 (2017).
@@
         \bibitem {10}
-        Oguego, C., Augusto, J., Muñ`oz, A., Springett, M.: A survey on managing users’ preferences in ambient intelligence. Universal Access in the Information Society. (2017).
+        Oguego, C., Augusto, J., Muñoz, A., Springett, M.: A survey on managing users’ preferences in ambient intelligence. Universal Access in the Information Society. (2017).
 
@@
         Ospan, B.: Simulation of a Simple Bio-Mimetic Robot with Neuromorphic Control System and Optimization Based on the Genetic Algorithm.
-International Journal of Innovations in Engineering and Technology.
+Int.
+Journal of Innovations in Engineering and Technology.
 8, 59-65 (2017).
